### 2023-05-21 paper.Rmd
initial commit

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on . 
abstract: |
  We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared. Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published. For the whole population of registrations on the OSF before November 2017 we estimate 58% is published. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. It is often challenging to identify whether public registrations are published due to a lack of information in registrations. In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our project shows a substantial amount of data that researchers collect is never publicly shared. Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature. Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published. The OSF has a policy to make all registrations public after four years. This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years. A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.

keywords          : "Publication Bias; File-Drawer; Registry; Research Waste"
wordcount         : "1111"
bibliography      : ["RegistriesPublication.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
figsintext        : yes
class             : "jou, a4paper"
output            : papaja::apa6_pdf
link-citations    : true
editor_options: 
  chunk_output_type: console
---

```{r load packages and data, include = FALSE}
# Load packages ----

library(readxl)
library(dplyr)
library(papaja)
library(binom)

# Load datafile ----

registration_data <- read_excel("registration_data.xlsx")

```

Scientists selectively publish studies they perform [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959]. Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions [@easterbrook_publication_1991; @lishner_sorting_2021]. Research resources are wasted when studies that have the potential to contribute to scientific knowledge go unpublished, [@buxton_avoiding_2021; @chalmers_avoidable_2009].

The practice of selective reporting has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@fanelli_positive_2010; @franco_publication_2014; @gerber_publication_2010]. It is challenging to quantify how many studies remain unpublished. The most accurate estimates come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. Dickersin and colleagues observed that from all 737 studies submitted to John Hopkins institutional review boards of the school of medicine and health 81% and 66% were published, respectively [@dickersin_factors_1992]. Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979, 93% was published after a decade [@dickersin_nih_1993]. In the only inception cohort study in the social sciences we know of, Franco et al. (2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database. An example of such a study registry is ClinicalTrials.gov [@dickersin_evolution_2012]. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013]. The OSF offers researchers the possibility to voluntarily preregister their study by specifying their hypotheses, methods, and statistical analysis plan.

One interesting aspect of preregistrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ]. This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of preregistered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

# The current study

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform, it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By examining the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable. This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not. 
Finally, while it is useful to quantify how many preregistered studies remain unpublished after four years, it is also important to understand why studies remain unpublished. The fourth aim of our study was to contacted the authors of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.

```{r registry info, include = FALSE}
load("res_df_data.RData")
load("author_df.RData")

colnames(res_df) <-  c("reg_id", "reg_date_created", "reg_date_modified", "reg_date_registered", "reg_date_registered", "category", "description", "fork", "public", "reg_withdrawn", "reg_withdrawal_justification", "has_project", "parent_project", "project_id", "web_address", "project_created", "project_modified", "project_title", "project_public")

tot_res <- cbind(res_df, author_df)

# Number of parent projects
length(res_df$parent_project)
# 9721 projects closed and or withdrawn
sum(res_df$project_id == "NA")
# 8008 projects public
sum(res_df$project_public == TRUE)

# Total closed is total not public - total withdrawn = 9042
total_closed <- sum(res_df$project_id == "NA") - sum(res_df$reg_withdrawn == TRUE)
total_closed
# Total open 8008
total_open <- sum(res_df$project_public == TRUE)
total_open

```

# Method

*Data sources*: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Researchers might still work on projects four years after a registration. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

```{r inclusion, include = FALSE}

# I need to fix the issue of number of included before and after emails.
# We included more first, and emailed people, and then removed some data.

# Table 2 with reasons for exclusions ----

excl_table <- registration_data %>% group_by(classification) %>% summarise_at(c("withdrawn", "no_research_study", "no_unique_study", "no_preregistration", "registered_report", "replication_project"), sum)
# Note that the sum in this table is higher than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.

# Select only included studies ----

# select only the 171 included studies
registration_data_included <- registration_data[which(registration_data$no_research_study == 0 & registration_data$withdrawn == 0 & registration_data$no_unique_study == 0 & registration_data$no_preregistration == 0 & registration_data$registered_report == 0 & registration_data$replication_project == 0), ]

# Total registrations included in the study
total_included <- nrow(registration_data_included)

# Percentage included before and after emails for Table 1 ----

included_before <- registration_data %>% group_by(classification) %>% summarise(sum_before = sum(included_before_emails), binom::binom.confint(x = sum(included_before_emails), n = length(classification), tol = 1e-8, method = "wilson"))

included_after <- registration_data %>% group_by(classification) %>% summarise(sum_after = sum(included_after_emails), binom::binom.confint(x = sum(included_after_emails), n = length(classification), tol = 1e-8, method = "wilson"))

included_table <- cbind(included_before$sum_before, 100*included_before$mean, included_after$sum_after, 100*included_after$mean, included_after$n)

rownames(included_table) <- c(paste("Manually Opened (n = ", included_after$n[1], ")", sep = ""), paste("Automatically Opened (n = ", included_after$n[2], ")", sep = ""))
colnames(included_table) <- c("Included Before Emails", "Percentage Before Emails", "Included After Emails", "Percentage After Emails", "Total")
included_table

# How often did we conclude the registration was published, not published, or uncertain? ----

table(registration_data_included$published_before_email)
# Based on an extensive search (see supplement) we classified 68 out of the 169 registrations as published, and 71 articles are unpublished. For 30 articles, we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, and there was very little information in the registration.

# Table 2 with reasons for exclusions ----

excl_table <- as.data.frame(registration_data %>% group_by(classification) %>% summarise_at(c("withdrawn", "no_research_study", "no_unique_study", "no_preregistration", "registered_report", "replication_project"), sum))[,2:7]
rownames(excl_table) <- c("Manually Opened", "Automatically Opened")
colnames(excl_table) <- c("Withdrawn", "No Research Study", "No Unique Study", "No Registration", "Registered Report", "Replication Project")
excl_table
# Note that the sum in this table is higher than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.

```

*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the preregistration was made public by the researchers, and 150 for which the preregistration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF preregistrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

*Classifying Publication Status*: Studies can be accessible in different degrees of accessibility, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis. We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. This use of the term ‘published’ differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

# Results

*Inclusion criteria*: After some projects were reclassified during the data analysis in total `r sum(included_after$n)` randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations. As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper. We therefore aimed to remove all registrations that were performed for practice purposes (e.g. student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication). Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022]. For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a preregistration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.

The number of included and excluded registrations in the sample is summarized in Table \@ref(tab:table-included). We originally included `r sum(included_before$sum_before)` registrations. After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, or being performed without the goal of publishing the data, our final sample size consists of `r sum(included_after$sum_after)` registrations, where for `r included_after$sum_after[1]` registrations the main project was public and for `r included_after$sum_after[2]` registrations the main project was not public.  An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \@ref(tab:table-excluded).

```{r table-included, echo = FALSE}
apa_table(t(included_table), digits = 0, caption = "Studies included in the analysis before and after e-mailing researchers.", note = "The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.")
```

```{r table-excluded, echo = FALSE}
apa_table(t(excl_table), digits = 0, caption = "Reasons studies were excluded from the analysis.")
```

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` articles as unpublished, and for `r table(registration_data_included$published_before_email)[4]` articles we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.

```{r email_responses, include = FALSE}
# We contacted 109 researchers

contacted_researchers <- sum(registration_data$email_response != "-")

# 29 authors with registrations associated with public OSF projects and 80 authors with registrations associated with closed OSF projects

contacted_researchers_per_group <- registration_data %>% group_by(classification) %>% summarise(sum = sum(email_response != "-"))

# of which 24 and 53 replied to our email with additional information to update our classification.

replies_per_group <- registration_data %>% group_by(classification) %>% summarise(sum = sum(email_response == 1))
percentage_responded <- contacted_researchers_per_group[,2] / contacted_researchers

# Responses by initial publication classification before emails
contacted_researchers_per_publication_status <- registration_data %>% group_by(published_before_email) %>% summarise(sum = sum(email_response != "-"))
responses_per_publication_status <- registration_data %>% group_by(published_before_email) %>% summarise(sum = sum(email_response == 1))

```

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the authors. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` authors with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*percentage_responded$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*percentage_responded$sum[2],2)`%) replied to our email with additional information to update our classification. We sent `r contacted_researchers_per_publication_status$sum[2]` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r responses_per_publication_status$sum[2]` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses). Two additional authors replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

```{r match, include = FALSE}

match_per_group <- registration_data %>% group_by(classification) %>% summarise(no_match = sum(match == 0), match = sum(match == 1))
match_per_group

sum(registration_data$match == 0)
sum(registration_data$match == 1)

sum(registration_data_included$match != "-")

# How many did we correctly classify when we thought they were published (1), unpublished (2), and when we were uncertain (3)?
match_per_classification <- registration_data %>% group_by(published_before_email) %>% summarise(no_match = sum(match == 0), match = sum(match == 1))

match_per_classification_by_category <- registration_data %>% group_by(published_before_email, classification) %>% summarise(no_match = sum(match == 0), match = sum(match == 1))

# add total column to compute percentages
match_per_classification_by_category$total <- match_per_classification_by_category$no_match + match_per_classification_by_category$match
match_per_classification_by_category$no_match_percentage <- match_per_classification_by_category$no_match/match_per_classification_by_category$total
match_per_classification_by_category$match_percentage <- match_per_classification_by_category$match/match_per_classification_by_category$total

```

After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%. Sometimes a publication we found in the literature did not belong to the preregistration. If the study associated with the registration was published in another article than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found. For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.

We received `r sum(match_per_classification[4,2:3])` responses for registrations we were uncertain about, and these follow-up emails indicated that `r match_per_classification[4,3]` (`r round(100*match_per_classification[4,3]/sum(match_per_classification[4,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.

Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found. Of the `r match_per_classification[4,2]` cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their preregistration on the OSF.

```{r published, include = FALSE}

# How many are published after email when we thought before emailing they were published (1), unpublished (2), and when we were uncertain (3)? Divide this per classification (manually opened and automatically opened) and whether we got an email response. 
published_after_email_per_classification <- registration_data_included %>% group_by(published_before_email, email_response, classification) %>% summarise(published = sum(published_after_email == 1), not_published = sum(published_after_email == 2), unsure = sum(published_after_email == 3))
published_after_email_per_classification

# How many did we think unpublished before emails?
total_assumed_unpublished <- sum(published_after_email_per_classification$published[5:8], published_after_email_per_classification$not_published[5:8])

# Of those, how many did we get a reply for?
total_assumed_unpublished_responses <- sum(published_after_email_per_classification$published[7:8], published_after_email_per_classification$not_published[7:8])

# Of those, how many did we not get a reply for?
total_assumed_unpublished_no_responses <- sum(published_after_email_per_classification$published[5:6], published_after_email_per_classification$not_published[5:6])

# For the 45 we got responses about, 14 were actually published, and 31 were not.
sum(published_after_email_per_classification$published[7:8])
sum(published_after_email_per_classification$not_published[7:8])

# Of the 14 published, 6 were from automatically opened registrations, out of 29 total closed projects, so 6/29 automatically opened projects we thought were unpublished were published. For the manually opened projects, 8/16 were published.
published_after_email_per_classification$published[7]
published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]
published_after_email_per_classification$published[8]
published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]

# We did not get responses for 26 projects, of which 22 were automatically opened, and 4 were manually opened, for which the following might hold: 
# 8/16 of the 4 manually opened registrations could be published.
# 6/29 of the 22 automatically opened registrations could be published
total_assumed_unpublished_no_responses
published_after_email_per_classification$not_published[5]
published_after_email_per_classification$not_published[6]

published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]

published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]

# So how many of the assumed unpublished are actually published?
published_non_response_unpublished <- ((published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]) + (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]))

unpublished_non_response_unpublished <- total_assumed_unpublished_no_responses - ((published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]) + (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]))

# Now for uncertain projects

# How many were we uncertain about before emails? 30
total_assumed_unpublished_uncertain <- sum(published_after_email_per_classification$published[9:12], published_after_email_per_classification$not_published[9:12], published_after_email_per_classification$unsure[9:12])

# Of those, how many did we get a reply for?
total_assumed_unpublished_uncertain_responses <-  sum(published_after_email_per_classification$published[11:12], published_after_email_per_classification$not_published[11:12], published_after_email_per_classification$unsure[11:12])

# Of those, how many did we not get a reply for?
total_assumed_unpublished_uncertain_no_responses <-  sum(published_after_email_per_classification$published[9:10], published_after_email_per_classification$not_published[9:10], published_after_email_per_classification$unsure[9:10])

# For the 24 we got responses about, 12 were actually published, and 12 were not.
sum(published_after_email_per_classification$published[11:12])
sum(published_after_email_per_classification$not_published[11:12])

#Of the 14 published, 6 were from automatically opened registrations, out of 29 total closed projects, so 6/29 automatically opened projects we thought were unpublished were published. For the manually opened projects, 8/16 were published.
published_after_email_per_classification$published[11]
published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]
published_after_email_per_classification$published[12]
published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]

# We did not get a response for 6 projects we were uncertain about, of which 1 was manually opened, and 5 were automatically opened. For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not. For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 10 were published. We did not get responses for 6 projects, of which 5 were automatically opened, and 1 was manually opened, for which the following might hold:

total_assumed_unpublished_uncertain_no_responses
published_after_email_per_classification$unsure[9]
published_after_email_per_classification$unsure[10]

published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]

published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]

# So how many of the uncertain registrations are actually published?
published_non_response_uncertain <- (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10])

unpublished_non_response_uncertain <- total_assumed_unpublished_uncertain_no_responses - ((published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]))

# For manually opened registrations, altogether the % of published studies is:

published_manual <- published_after_email_per_classification$published[2] + published_after_email_per_classification$published[4] + published_after_email_per_classification$published[7] + published_after_email_per_classification$published[11] + published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5] + published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]

# For automatically opened registrations (classification 2), altogether the % of published studies is: 
# 6 we classified as published, 6 published we thought unpublished but confirmed in email response, +9 confirmed unpublished we were uncertain about, + 5 * 9/19 for the 5 unsure without response, and those we thought unpublished predicted to be published. 
published_auto <- published_after_email_per_classification$published[3] + published_after_email_per_classification$published[8] + published_after_email_per_classification$published[12] + published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10] + published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]

# And the unpublished studies for manually opened registrations is:
unpublished_manual <- published_after_email_per_classification$not_published[7] + published_after_email_per_classification$not_published[11] + (1 - (published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]))) * published_after_email_per_classification$not_published[5] + (1 - (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]))) * published_after_email_per_classification$unsure[9]

# And the unpublished automatically opened studies are:
unpublished_auto <- published_after_email_per_classification$not_published[8] + published_after_email_per_classification$not_published[12] + (1 - (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]))) * published_after_email_per_classification$not_published[6] + (1 - (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]))) * published_after_email_per_classification$unsure[10]

# Check to see if they combine to 169 total included:
published_manual + published_auto + unpublished_manual + unpublished_auto

# Compute CI around estimates per group
result_total <- binom.confint(x = published_manual + published_auto, n = published_manual + unpublished_manual + published_auto + unpublished_auto, tol = 1e-8, method = "wilson")
result_manual <- binom.confint(x = published_manual, n = published_manual + unpublished_manual, tol = 1e-8, method = "wilson")
result_auto <- binom.confint(x = published_auto, n = published_auto + unpublished_auto, tol = 1e-8, method = "wilson")

```

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r unpublished_non_response_unpublished` out of `r total_assumed_unpublished_no_responses` of the registration in the unpublished classification and `r unpublished_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` of the registration in the uncertain classification are actually published.

```{r table-estimated-nonpublication}
# Estimates of (non-)publication ------------------------------------------

estimated_nonpublication <- data.frame(Group = c("Manually Opened", "Automatically Opened", "Total"),
                 Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
                 Percentage_Included = c(round(included_before$mean,2), ""),
                 Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
                 Published = c(round(result_manual$mean,2), round(result_auto$mean,2), ""), 
                 Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
                 Non_Published_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))) - c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0)
                 )
colnames(estimated_nonpublication) <- c("Group", "Registrations", "% Included", "Included", "% Published", "Published", "Not Published")
apa_table(estimated_nonpublication, digits = 0, caption = "Estimated number of published and unpublished studies registered on the OSF before November 2017.")
```

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]). This sample contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations. Multiplying our publications estimates by the estimated number of research studies registered on the OSF before November 2017 we see `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100 * estimated_nonpublication[3,6] / (estimated_nonpublication[3,6] + estimated_nonpublication[3,7]),2)`% of registrations are published as an article, preprint, thesis, or poster after at least four years.

```{r reasons_non_publish, include = FALSE}
# Reason not published ----------------------------------------------------

# It matters if this is done on all registrations we emailed for, or just the ones we ended up including.

reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(results = sum(reason_if_unpublished == 1 | reason_if_unpublished == 4 | reason_if_unpublished == 11), review = sum(reason_if_unpublished == 3 | reason_if_unpublished == 14), not_goal_to_publish = sum(reason_if_unpublished == 6 | reason_if_unpublished == 7 | reason_if_unpublished == 9), planning = sum(reason_if_unpublished == 2 | reason_if_unpublished == 5 | reason_if_unpublished == 8 | reason_if_unpublished == 10 | reason_if_unpublished == 13 | reason_if_unpublished == 15 | reason_if_unpublished == 16), study_design = sum(reason_if_unpublished == 12))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("Results", "Peer Review", "Not Goal to Publish", "Planning", "Study Design")

```

# Evaluating the Effect of Automatically Making Registries Public

We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy, were classified as manually opened by the researchers have been published. In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that `r round(100*result_auto[4], 2)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 2)`] of automatically opened registrations is published. Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

# Why do studies remained unpublished?

When registrations were classified as unpublished, or when we were uncertain about whether a registration was published, we reached out to the researchers to ask them whether their registration was published or not, and if not, why it remained unpublished. We also asked why they made the corresponding OSF project public or why they kept it private, and if the researchers were aware that the OSF would automatically make their registration public after four years. This study was approved by the ERB at Eindhoven University of Technology under proposal number 1674.

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the Supplementary Material). Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).

According to the responses we received, issues related to ‘planning’ are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

```{r table-reasons, echo = FALSE}

apa_table(t(reasons_table), digits = 0, caption = "Summary of main reasons researchers self-reported to not publish registered studies.", note = "Only the first or main reason was coded whenever respondents gave multiple reasons.")

```

```{r reasons_open_project, include = FALSE}

reasons_open_project_table <- registration_data %>% summarise(open_science = sum(motivation_opening_project == 1 | motivation_opening_project == 6 | motivation_opening_project == 7), technical_issues = sum(motivation_opening_project == 2 | motivation_opening_project == 4), other = sum(motivation_opening_project == 3 | motivation_opening_project == 5))
reasons_open_project_table <- as.data.frame(reasons_open_project_table)
rownames(reasons_open_project_table) <- c("Reasons")
colnames(reasons_open_project_table) <- c("Open Science", "Technical Issues", "Other")

reasons_open_project_table[2]
sum(reasons_open_project_table)

reasons_closed_project_table <- registration_data %>% summarise(results = sum(motivation_not_opening_project == 1), publication_process = sum(motivation_not_opening_project == 2 | motivation_not_opening_project == 10), no_new_information = sum(motivation_not_opening_project == 4 | motivation_not_opening_project == 5 | motivation_not_opening_project == 7 | motivation_not_opening_project == 8 | motivation_not_opening_project == 9 | motivation_not_opening_project == 14), planning = sum(motivation_not_opening_project == 11 | motivation_not_opening_project == 6), technical_issues = sum(motivation_not_opening_project == 12 | motivation_not_opening_project == 13), forgotten = sum(motivation_not_opening_project == 3), other = sum(motivation_not_opening_project == 15 | motivation_not_opening_project == 16))
reasons_closed_project_table <- as.data.frame(reasons_closed_project_table)
rownames(reasons_closed_project_table) <- c("Reasons")
colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Planning", "Technical Issues", "Forgotten", "Other")
reasons_closed_project_table

sum(registration_data$four_years_known == 1)
sum(registration_data$four_years_known == 0)

```

When asked why researchers made their OSF project page open, most researchers (`r reasons_open_project_table[2]` out of `r sum(reasons_open_project_table)` mentioned a motivation to practice open science. Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), waiting until a project was published (`r reasons_closed_project_table[2]` times), and technical issues (`r reasons_closed_project_table[5]` times). Finally, we were interested in how many researchers who preregistered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years. Although not all of the email respondents answered this question, `r sum(registration_data$four_years_known == 1)` of the researchers indicated they were aware of this policy, and `r sum(registration_data$four_years_known == 0)` were not aware of this policy.

# Discussion

Our examination of `r sum(included_after$sum_after)` registration on the Open Science framework created before November 18, 2017, led to an estimated (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]) of registrations that were published. Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_total[4], 2)`% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the results (e.g., null results or failed replications) were the reason that the study remained unpublished are concerning in light of the possibility that the absence of these studies contributed to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014]. Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results [@allen_open_2019; @scheel_excess_2021]. If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent. With the rise of data repositories and preprints it has become feasible and easy to share the results of studies, although future work that makes it easier to find, evaluate, and integrate study results is important.

It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study. First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report. Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017. The practice to register studies is becoming more widespread, but up to 2017 was predominantly done by early adopters interested in open science practices. It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not preregister in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer. We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published. Registering a study requires work, and it possible that researchers only register studies they feel have a higher probability of being submitted for publication. Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines. The probability that researchers have the time to share data from a registered study might change over time, and could for example be in recent years due to the COVID pandemic. In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.

However, our goal was not to establish a generalizable estimate. The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large. At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, failed replications) play a role in many (if not all) scientific contexts. Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be few unpublished studies. In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample. Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.

*Recommendations for Registries*. We found that registrations are sometimes used to create a stable repository after a study has been completed, and sometimes to register the existence (and sometimes methodological details) of a planned study. To be able to distinguish these to uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘prospective registration’ or ‘preregistration’ from ‘post registration’ or ‘data archiving’). A third registration option should be created for all registrations that are done for purely educational or practice purposes. The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years.  Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations. Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.

*Recommendations for Registry Users*. Researchers should be aware that the OSF only makes the registration public, but not the main project page. This means that, for example, in the “OSF-Standard Pre-Data Collection Registration” the only information that becomes visible is the answer to the question “Has data collection begun for this project?”, the answer to the question “Have you looked at the data?”, and the text in the field “Other comments”. Some users wrote in this field “See the preregistration document specifying the logic, hypotheses, and analyses” but that files is not made accessible. If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the “Other comments” field. It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration [@akker_effectiveness_2023] and to create machine-readable analysis code that describe when statistical hypotheses are corroborated or falsified [@lakens_improving_2021]. Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed. Adding an ORCID ID (for example to your OSF profile) and an email address (while realizing that researchers do not stay at the same institution indefinitely) is good practice.

# Conclusion

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and it is difficult to judge whether the percentage of unpublished data we observed in our sample is too high. What is perhaps most surprising is that researchers rarely talk about how many datasets they have collected that could have value for peers but that nevertheless linger in their filedrawer. Researchers might not feel like they can frankly discuss this topic due to the association of unpublished studies with publication bias. Although we found publication bias to be one reason to not share data, logistical issues were more commonly provided as a reason not to share data. More transparency about unpublished datasets would allow our field to learn and improve the way we work, and improve practices to increase the efficiency of psychological science.

# References

<!-- # interlinepenalty prevents freak error when a hyperlink in reference breaks across a page -->
\begingroup
\interlinepenalty = 10000

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2023-05-21 paper.tex
initial commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ,jou, a4paper,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Publication Bias; File-Drawer; Registry; Research Waste\newline\indent Word count: 1111}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
  pdfauthor={Eline Ensinck1 \& Daniël Lakens1},
  pdflang={en-EN},
  pdfkeywords={Publication Bias; File-Drawer; Registry; Research Waste},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
\author{Eline Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
\date{}

\shorttitle{QUANTIFYING PUBLISHED REGISTERED STUDIES}

\authornote{

This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript, are available at \url{https://github.com/Lakens/xxx}.

Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, 5600MB Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Eindhoven University of Technology}

\abstract{%
We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared. Examining 315 registrations revealed that 169 were research studies, of which 104 (62\%) were published. For the whole population of registrations on the OSF before November 2017 we estimate 58\% is published. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. It is often challenging to identify whether public registrations are published due to a lack of information in registrations. In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our project shows a substantial amount of data that researchers collect is never publicly shared. Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature. Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published. The OSF has a policy to make all registrations public after four years. This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years. A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.
}

\begin{document}
\maketitle

Scientists selectively publish studies they perform (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}). Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions (\protect\hyperlink{ref-easterbrook_publication_1991}{Easterbrook, Berlin, Gopalan, \& Matthews, 1991}; \protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). Research resources are wasted when studies that have the potential to contribute to scientific knowledge go unpublished, (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).

The practice of selective reporting has been demonstrated in various disciplines, ranging from psychology and sociology to economics (\protect\hyperlink{ref-fanelli_positive_2010}{Fanelli, 2010}; \protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}). It is challenging to quantify how many studies remain unpublished. The most accurate estimates come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}). Dickersin and colleagues observed that from all 737 studies submitted to John Hopkins institutional review boards of the school of medicine and health 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}). Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979, 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}). In the only inception cohort study in the social sciences we know of, Franco et al.~(2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.

One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database. An example of such a study registry is ClinicalTrials.gov (\protect\hyperlink{ref-dickersin_evolution_2012}{Dickersin \& Rennie, 2012}). The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain (\protect\hyperlink{ref-spies_open_2013}{Spies, 2013}). The OSF offers researchers the possibility to voluntarily preregister their study by specifying their hypotheses, methods, and statistical analysis plan.

One interesting aspect of preregistrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) will be made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}. This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of preregistered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

\hypertarget{the-current-study}{%
\section{The current study}\label{the-current-study}}

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform, it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By examining the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable. This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
Finally, while it is useful to quantify how many preregistered studies remain unpublished after four years, it is also important to understand why studies remain unpublished. The fourth aim of our study was to contacted the authors of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.

\hypertarget{method}{%
\section{Method}\label{method}}

\emph{Data sources}: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Researchers might still work on projects four years after a registration. The final classification was based on whether the projects were public in April 2022. For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project is private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the preregistration was made public by the researchers, and 150 for which the preregistration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF preregistrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

\emph{Classifying Publication Status}: Studies can be accessible in different degrees of accessibility, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). We considered a study `published' if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis. We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. This use of the term `published' differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

\hypertarget{results}{%
\section{Results}\label{results}}

\emph{Inclusion criteria}: After some projects were reclassified during the data analysis in total 315 randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for 164 registrations and the associated project was closed for 151 registrations. As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper. We therefore aimed to remove all registrations that were performed for practice purposes (e.g.~student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication). Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}). For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a preregistration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.

The number of included and excluded registrations in the sample is summarized in Table \ref{tab:table-included}. We originally included 176 registrations. After excluding 7 registrations based on email responses for being student projects, or being performed without the goal of publishing the data, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public. An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \ref{tab:table-excluded}.

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table-included}Studies included in the analysis before and after e-mailing researchers.}

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Manually Opened (n = 164)} & \multicolumn{1}{c}{Automatically Opened (n = 151)}\\
\midrule
Included Before Emails & 90 & 86\\
Percentage Before Emails & 55 & 57\\
Included After Emails & 88 & 81\\
Percentage After Emails & 54 & 54\\
Total & 164 & 151\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table-excluded}Reasons studies were excluded from the analysis.}

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened}\\
\midrule
Withdrawn & 1 & 5\\
No Research Study & 21 & 50\\
No Unique Study & 13 & 5\\
No Registration & 27 & 20\\
Registered Report & 13 & 3\\
Replication Project & 12 & 1\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

\emph{Identifying Publications Corresponding to Registrations}: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 articles as unpublished, and for 30 articles we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the authors. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted 109 researchers, 29 authors with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (26.61\%) and 53 (73.39\%) replied to our email with additional information to update our classification. We sent 1 email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received 1 response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses). Two additional authors replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the preregistration. If the study associated with the registration was published in another article than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.

We received 25 responses for registrations we were uncertain about, and these follow-up emails indicated that 11 (44\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.

Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their preregistration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 19.45 out of 26 of the registration in the unpublished classification and 3.03 out of 6 of the registration in the uncertain classification are actually published.

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table-estimated-nonpublication}Estimated number of published and unpublished studies registered on the OSF before November 2017.}

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{Registrations} & \multicolumn{1}{c}{\% Included} & \multicolumn{1}{c}{Included} & \multicolumn{1}{c}{\% Published} & \multicolumn{1}{c}{Published} & \multicolumn{1}{c}{Not Published}\\
\midrule
Manually Opened & 8008 & 0.55 & 4,395 & 0.86 & 3,775 & 619\\
Automatically Opened & 9042 & 0.57 & 5,150 & 0.34 & 1,775 & 3,375\\
Total & 17050 &  & 9,544 &  & 5,550 & 3,994\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}). This sample contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations. Multiplying our publications estimates by the estimated number of research studies registered on the OSF before November 2017 we see 5550 registrations are published, and 3994 remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\% of registrations are published as an article, preprint, thesis, or poster after at least four years.

\hypertarget{evaluating-the-effect-of-automatically-making-registries-public}{%
\section{Evaluating the Effect of Automatically Making Registries Public}\label{evaluating-the-effect-of-automatically-making-registries-public}}

We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy, were classified as manually opened by the researchers have been published. In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that 34.47\%, 95\% CI {[}25.04; 45.31{]} of automatically opened registrations is published. Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

\hypertarget{why-do-studies-remained-unpublished}{%
\section{Why do studies remained unpublished?}\label{why-do-studies-remained-unpublished}}

When registrations were classified as unpublished, or when we were uncertain about whether a registration was published, we reached out to the researchers to ask them whether their registration was published or not, and if not, why it remained unpublished. We also asked why they made the corresponding OSF project public or why they kept it private, and if the researchers were aware that the OSF would automatically make their registration public after four years. This study was approved by the ERB at Eindhoven University of Technology under proposal number 1674.

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the Supplementary Material). Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).

According to the responses we received, issues related to `planning' are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table-reasons}Summary of main reasons researchers self-reported to not publish registered studies.}

\begin{tabular}{llll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened} & \multicolumn{1}{c}{Total}\\
\midrule
Results & 3 & 11 & 14\\
Peer Review & 6 & 5 & 11\\
Not Goal to Publish & 0 & 2 & 2\\
Planning & 7 & 18 & 25\\
Study Design & 1 & 2 & 3\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only the first or main reason was coded whenever respondents gave multiple reasons.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

When asked why researchers made their OSF project page open, most researchers (2 out of 23 mentioned a motivation to practice open science. Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (15 times), researchers forgot to open it (11 times), waiting until a project was published (6 times), and technical issues (4 times). Finally, we were interested in how many researchers who preregistered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years. Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Our examination of 169 registration on the Open Science framework created before November 18, 2017, led to an estimated (61.25\%, 95\% CI {[}53.74; 68.27{]}) of registrations that were published. Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 38.75\% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

The fact that for 20\% of unpublished studies researchers indicated that the results (e.g., null results or failed replications) were the reason that the study remained unpublished are concerning in light of the possibility that the absence of these studies contributed to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}). Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}). If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent. With the rise of data repositories and preprints it has become feasible and easy to share the results of studies, although future work that makes it easier to find, evaluate, and integrate study results is important.

It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study. First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report. Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017. The practice to register studies is becoming more widespread, but up to 2017 was predominantly done by early adopters interested in open science practices. It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not preregister in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer. We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published. Registering a study requires work, and it possible that researchers only register studies they feel have a higher probability of being submitted for publication. Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines. The probability that researchers have the time to share data from a registered study might change over time, and could for example be in recent years due to the COVID pandemic. In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.

However, our goal was not to establish a generalizable estimate. The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large. At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, failed replications) play a role in many (if not all) scientific contexts. Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be few unpublished studies. In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample. Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.

\emph{Recommendations for Registries}. We found that registrations are sometimes used to create a stable repository after a study has been completed, and sometimes to register the existence (and sometimes methodological details) of a planned study. To be able to distinguish these to uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving'). A third registration option should be created for all registrations that are done for purely educational or practice purposes. The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years. Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations. Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.

\emph{Recommendations for Registry Users}. Researchers should be aware that the OSF only makes the registration public, but not the main project page. This means that, for example, in the ``OSF-Standard Pre-Data Collection Registration'' the only information that becomes visible is the answer to the question ``Has data collection begun for this project?'', the answer to the question ``Have you looked at the data?'', and the text in the field ``Other comments''. Some users wrote in this field ``See the preregistration document specifying the logic, hypotheses, and analyses'' but that files is not made accessible. If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the ``Other comments'' field. It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration (\protect\hyperlink{ref-akker_effectiveness_2023}{Akker et al., 2023}) and to create machine-readable analysis code that describe when statistical hypotheses are corroborated or falsified (\protect\hyperlink{ref-lakens_improving_2021}{Lakens \& DeBruine, 2021}). Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed. Adding an ORCID ID (for example to your OSF profile) and an email address (while realizing that researchers do not stay at the same institution indefinitely) is good practice.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and it is difficult to judge whether the percentage of unpublished data we observed in our sample is too high. What is perhaps most surprising is that researchers rarely talk about how many datasets they have collected that could have value for peers but that nevertheless linger in their filedrawer. Researchers might not feel like they can frankly discuss this topic due to the association of unpublished studies with publication bias. Although we found publication bias to be one reason to not share data, logistical issues were more commonly provided as a reason not to share data. More transparency about unpublished datasets would allow our field to learn and improve the way we work, and improve practices to increase the efficiency of psychological science.

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup

\interlinepenalty = 10000

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-akker_effectiveness_2023}{}}%
Akker, O. van den, Bakker, M., Assen, M. A. L. M. van, Pennington, C. R., Verweij, L., Elsherif, M., \ldots{} Wicherts, J. (2023). \emph{The effectiveness of preregistration in psychology: {Assessing} preregistration strictness and preregistration-study consistency}. {MetaArXiv}. \url{https://doi.org/10.31222/osf.io/h8xjw}

\leavevmode\vadjust pre{\hypertarget{ref-allen_open_2019}{}}%
Allen, C., \& Mehler, D. M. A. (2019). Open science challenges, benefits and tips in early career and beyond. \emph{PLOS Biology}, \emph{17}(5), e3000246. \url{https://doi.org/10.1371/journal.pbio.3000246}

\leavevmode\vadjust pre{\hypertarget{ref-bernal_social_1939}{}}%
Bernal, J. D. (1939). \emph{The {Social Function Of Science}}. {London}: {Routledge}.

\leavevmode\vadjust pre{\hypertarget{ref-buxton_avoiding_2021}{}}%
Buxton, R. T., Nyboer, E. A., Pigeon, K. E., Raby, G. D., Rytwinski, T., Gallagher, A. J., \ldots{} Roche, D. G. (2021). Avoiding wasted research resources in conservation science. \emph{Conservation Science and Practice}, \emph{3}(2), e329. \url{https://doi.org/10.1111/csp2.329}

\leavevmode\vadjust pre{\hypertarget{ref-chalmers_avoidable_2009}{}}%
Chalmers, I., \& Glasziou, P. (2009). Avoidable waste in the production and reporting of research evidence. \emph{The Lancet}, \emph{374}(9683), 86--89.

\leavevmode\vadjust pre{\hypertarget{ref-chambers_past_2022}{}}%
Chambers, C. D., \& Tzavella, L. (2022). The past, present and future of {Registered Reports}. \emph{Nature Human Behaviour}, \emph{6}(1), 29--42. \url{https://doi.org/10.1038/s41562-021-01193-7}

\leavevmode\vadjust pre{\hypertarget{ref-dickersin_nih_1993}{}}%
Dickersin, K., \& Min, Y. I. (1993). \href{https://www.ncbi.nlm.nih.gov/pubmed/8306005}{{NIH} clinical trials and publication bias}. \emph{The Online Journal of Current Clinical Trials}, \emph{Doc No 50}, {[}4967 words; 53 paragraphs{]}.

\leavevmode\vadjust pre{\hypertarget{ref-dickersin_factors_1992}{}}%
Dickersin, K., Min, Y. I., \& Meinert, C. L. (1992). \href{https://www.ncbi.nlm.nih.gov/pubmed/1727960}{Factors influencing publication of research results. {Follow-up} of applications submitted to two institutional review boards}. \emph{JAMA}, \emph{267}(3), 374--378.

\leavevmode\vadjust pre{\hypertarget{ref-dickersin_evolution_2012}{}}%
Dickersin, K., \& Rennie, D. (2012). The {Evolution} of {Trial Registries} and {Their Use} to {Assess} the {Clinical Trial Enterprise}. \emph{JAMA}, \emph{307}(17), 1861--1864. \url{https://doi.org/10.1001/jama.2012.4230}

\leavevmode\vadjust pre{\hypertarget{ref-easterbrook_publication_1991}{}}%
Easterbrook, P. J., Berlin, J. A., Gopalan, R., \& Matthews, D. R. (1991). Publication bias in clinical research. \emph{Lancet (London, England)}, \emph{337}(8746), 867--872. \url{https://doi.org/10.1016/0140-6736(91)90201-y}

\leavevmode\vadjust pre{\hypertarget{ref-fanelli_positive_2010}{}}%
Fanelli, D. (2010). {``{Positive}''} {Results Increase Down} the {Hierarchy} of the {Sciences}. \emph{PLoS ONE}, \emph{5}(4). \url{https://doi.org/10.1371/journal.pone.0010068}

\leavevmode\vadjust pre{\hypertarget{ref-franco_publication_2014}{}}%
Franco, A., Malhotra, N., \& Simonovits, G. (2014). Publication bias in the social sciences: {Unlocking} the file drawer. \emph{Science}, \emph{345}(6203), 1502--1505. \url{https://doi.org/10.1126/SCIENCE.1255484}

\leavevmode\vadjust pre{\hypertarget{ref-gerber_publication_2010}{}}%
Gerber, A. S., Malhotra, N., Dowling, C. M., \& Doherty, D. (2010). Publication {Bias} in {Two Political Behavior Literatures}. \emph{American Politics Research}, \emph{38}(4), 591--613. \url{https://doi.org/10.1177/1532673X09350979}

\leavevmode\vadjust pre{\hypertarget{ref-greenwald_consequences_1975}{}}%
Greenwald, A. G. (1975). Consequences of prejudice against the null hypothesis. \emph{Psychological Bulletin}, \emph{82}(1), 1--20. \url{https://doi.org/10.1037/h0076157}

\leavevmode\vadjust pre{\hypertarget{ref-lakens_improving_2021}{}}%
Lakens, D., \& DeBruine, L. M. (2021). Improving {Transparency}, {Falsifiability}, and {Rigor} by {Making Hypothesis Tests Machine-Readable}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(2), 2515245920970949. \url{https://doi.org/10.1177/2515245920970949}

\leavevmode\vadjust pre{\hypertarget{ref-lishner_sorting_2021}{}}%
Lishner, D. A. (2021). Sorting the {File Drawer}: {A Typology} for {Describing Unpublished Studies}. \emph{Perspectives on Psychological Science}, 1745691620979831. \url{https://doi.org/10.1177/1745691620979831}

\leavevmode\vadjust pre{\hypertarget{ref-nosek_registered_2014}{}}%
Nosek, B. A., \& Lakens, D. (2014). Registered reports: {A} method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141. \url{https://doi.org/10.1027/1864-9335/a000192}

\leavevmode\vadjust pre{\hypertarget{ref-scheel_excess_2021}{}}%
Scheel, A. M., Schijen, M. R. M. J., \& Lakens, D. (2021). An {Excess} of {Positive Results}: {Comparing} the {Standard Psychology Literature With Registered Reports}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(2), 25152459211007467. \url{https://doi.org/10.1177/25152459211007467}

\leavevmode\vadjust pre{\hypertarget{ref-song_dissemination_2010}{}}%
Song, F., Parekh, S., Hooper, L., Loke, Y. K., Ryder, J., Sutton, A. J., \ldots{} Harvey, I. (2010). Dissemination and publication of research findings: An updated review of related biases. \emph{Health Technology Assessment (Winchester, England)}, \emph{14}(8), iii, ix--xi, 1--193. \url{https://doi.org/10.3310/hta14080}

\leavevmode\vadjust pre{\hypertarget{ref-spies_open_2013}{}}%
Spies, J. R. (2013). \emph{The open science framework: {Improving} science by making it open and accessible}. {University of Virginia}.

\leavevmode\vadjust pre{\hypertarget{ref-sterling_publication_1959}{}}%
Sterling, T. D. (1959). Publication {Decisions} and {Their Possible Effects} on {Inferences Drawn} from {Tests} of {Significance--Or Vice Versa}. \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34. \url{https://doi.org/10.2307/2282137}

\leavevmode\vadjust pre{\hypertarget{ref-van_elk_whats_2021}{}}%
van Elk, M. (2021). What's hidden in my filedrawer and what's in yours? {Disclosing} non-published findings in the cognitive science of religion. \emph{Religion, Brain \& Behavior}, \emph{11}(1), 5--16. \url{https://doi.org/10.1080/2153599X.2020.1729233}

\end{CSLReferences}

\endgroup

\end{document}

### 2023-05-21 supplement.Rmd
initial commit

---
title             : "Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "SUPPLEMENT"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript, are available at https://github.com/Lakens/xxx. 
abstract: |
  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive preregistrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.

keywords          : "Publication Bias; File-Drawer; Registry; Research Waste"
wordcount         : "1111"
bibliography      : ["RegistriesPublication.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
figsintext        : yes
class             : "jou, a4paper"
output            : papaja::apa6_pdf
link-citations    : true
editor_options: 
  chunk_output_type: console
---

```{r load packages and data, include = FALSE}
# Load packages ----

library(readxl)
library(dplyr)
library(papaja)
library(binom)

# Load datafile ----

registration_data <- read_excel("registration_data.xlsx")

registration_data_included <- registration_data[which(registration_data$no_research_study == 0 & registration_data$withdrawn == 0 & registration_data$no_unique_study == 0 & registration_data$no_preregistration == 0 & registration_data$registered_report == 0 & registration_data$replication_project == 0), ]

```

# Details on Classifying Registrations as a Research Study

It can be challenging to determine whether a registration was performed with the goal to publish a study. Sometimes, the description of the preregistration or project page explicitly revealed that a registration was not an actual research study (for instance, when the group number of the course was shared), or it explicitly linked to a final publication. When it was not clear from the description on the OSF if the registration concerned an actual research study, we searched for information about the author(s) on the OSF. If the person who registered the project had various activity points and projects on the OSF, we assumed this person was an active researcher, and not a student. If someone had used the OSF at most a few times since 2017, and did not provide any personal information, we tried to determine if the user was a researcher by searching for scientific publications or membership of research groups (e.g. profiles on institutional websites). If such information could be found, the registration was coded as an actual research study. If such information could not be found, the registration was marked as “no research study” (e.g., it was assumed to be a student assignment). In the case of multiple authors, it is possible that only a subgroup of the authors could be found. If only one of the authors seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF. However, if more than one author seemed to be an actual researcher, the registration was marked as an actual research study. These decisions necessarily introduce some arbitrariness in whether a study was intended to be published or not, and therefore we explored whether researchers intended to publish a study when we emailed researchers to follow up on unpublished registrations (see below).

We observed quite some variation in the amount of detail in the preregistrations that we examined. We therefore decided to code the ‘quality’ of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the preregistrations in both groups and check for possible differences that could lead to different publication rates.

# Details on Classifying Studies as Published or Not

```{r publicationtype}
# Reason not published ----------------------------------------------------

# It matters if this is done on all registrations we emailed for, or just the ones we ended up including.

publicationtype <- registration_data_included %>% group_by(classification) %>% summarise(journal = sum(journal_article_after_email == 1), preprint = sum(grey_literature_after_email == 1), thesis = sum(grey_literature_after_email == 2), poster = sum(grey_literature_after_email == 3), report = sum(grey_literature_after_email == 4), conference = sum(grey_literature_after_email == 5))
publicationtype[3,] <- publicationtype[1,] + publicationtype[2,]
publicationtype <- as.data.frame(publicationtype[,-1])
rownames(publicationtype) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(publicationtype) <- c("Journal Article", "Preprint", "PhD Thesis", "Poster", "Report", "Conference Proceeding")

apa_table(t(publicationtype), digits = 0, caption = "Type of object that matched the registration for all registrations that were publicly shared")

```

For each registration, we first searched for the combination of the title of the registration and the names of the authors in Google Scholar and examined the search results. We considered the registration published if it appeared as a journal article, preprint, PhD thesis in a repository, an online report, or conference proceedings. The frequency of each publication type is provided in Table \@ref(tab:publicationtype). When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the authors of the publication. We also searched the publication for a link to an OSF project page that was associated with the registration. If the publication indeed seemed to be about the same topic and was published after the registration date on the OSF, the study was marked as publicly shared.

Because titles of the registrations and papers often do not match we continued our search based on the names of the OSF users. For each user associated with a registration we retrieved a list of their publications and scanned through their publications after the registration date. If a paper similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine of the publication matched the registration. Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as “not publicly shared”.

Our use of the term ‘published’ differs from another inception cohort study in psychology [@franco_publication_2014] who limited 'publication' to journal articles and book chapters. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

When searching through the literature, different types of publications were found. To get an idea of the type of publications found within this sample, we distinguished between a journal article, preprint, PhD thesis, poster, draft/report, and conference paper. An overview is given in table xxx.

# Extensiveness of the details in registrations

```{r table-quality, echo = FALSE}

quality_reg <- as.data.frame.matrix(table(registration_data_included$classification, registration_data_included$quality_of_registration))
rownames(quality_reg) <- c("Manually Opened", "Automatically Opened")
colnames(quality_reg) <- c("Empty",	"Minimal", "Short", "Extensive")

apa_table(quality_reg, digits = 0, caption = "Classification of the extensiveness of registrations.")

```

Because of large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were. `r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration. At least a minimal description was given for `r round(100*quality_reg[1,2]/sum(quality_reg[1,]),0)`% of the registrations in the manually opened registrations and `r round(100*quality_reg[2,2]/sum(quality_reg[2,]),0)`% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in `r round(100*quality_reg[1,3]/sum(quality_reg[1,]),0)`% of the cases in the manually opened registrations and `r round(100*quality_reg[2,3]/sum(quality_reg[2,]),0)`% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (`r round(100*quality_reg[1,4]/sum(quality_reg[1,]),0)`% and `r round(100*quality_reg[2,4]/sum(quality_reg[2,]),0)`% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \@ref(tab:table-quality). The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of details in the registrations (and thus that of the research studies) does not differ much between the two groups.

# Fine-grained categorization of reasons for non-publication

In the main text we have classified the reasons provided by researchers not to publish in five categories. Below, we provide a more fine-grained classification consisting of 15 categories.

```{r reasons_non_publish}
# Reason not published ----------------------------------------------------

# It matters if this is done on all registrations we emailed for, or just the ones we ended up including.

reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(a = sum(reason_if_unpublished == 1), b = sum(reason_if_unpublished == 2), c = sum(reason_if_unpublished == 3), d = sum(reason_if_unpublished == 4), e = sum(reason_if_unpublished == 5), f = sum(reason_if_unpublished == 6), h = sum(reason_if_unpublished == 7), i = sum(reason_if_unpublished == 8), j = sum(reason_if_unpublished == 9), k = sum(reason_if_unpublished == 10), l = sum(reason_if_unpublished == 11), m = sum(reason_if_unpublished == 12), n = sum(reason_if_unpublished == 13), o = sum(reason_if_unpublished == 14), p = sum(reason_if_unpublished == 15), q = sum(reason_if_unpublished == 16))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("No significant results", "Left academia", "Paper rejected", "Failed replication", "Unfinished study", "Educational project", "Pilot", "Switched job / research directions", "Shared with funder (not the goal to publish)", "Lack of time / busy with other projects", "Conflicting / unclear results", "Flaws in procedure", "Still in progress", "Reviewers requested it", "Extra study (no priority)", "Health issues")

apa_table(t(reasons_table), digits = 0, caption = "Summary of main reasons researchers self-reported to not publish registered studies.", note = "Only the first or main reason was coded whenever respondents gave multiple reasons.")

```

```{r reasons_open_project, include = FALSE}

reasons_open_project_table <- registration_data %>% summarise(open_science = sum(motivation_opening_project == 1 | motivation_opening_project == 6 | motivation_opening_project == 7), technical_issues = sum(motivation_opening_project == 2 | motivation_opening_project == 4), other = sum(motivation_opening_project == 3 | motivation_opening_project == 5))
reasons_open_project_table <- as.data.frame(reasons_open_project_table)
rownames(reasons_open_project_table) <- c("Reasons")
colnames(reasons_open_project_table) <- c("Open Science", "Technical Issues", "Other")

reasons_closed_project_table <- registration_data %>% summarise(results = sum(motivation_not_opening_project == 1), publication_process = sum(motivation_not_opening_project == 2 | motivation_not_opening_project == 10), no_new_information = sum(motivation_not_opening_project == 4 | motivation_not_opening_project == 5 | motivation_not_opening_project == 7 | motivation_not_opening_project == 8 | motivation_not_opening_project == 9 | motivation_not_opening_project == 14), planning = sum(motivation_not_opening_project == 11 | motivation_not_opening_project == 6), technical_issues = sum(motivation_not_opening_project == 12 | motivation_not_opening_project == 13), forgotten = sum(motivation_not_opening_project == 3), other = sum(motivation_not_opening_project == 15 | motivation_not_opening_project == 16))
reasons_closed_project_table <- as.data.frame(reasons_closed_project_table)
rownames(reasons_closed_project_table) <- c("Reasons")
colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Planning", "Technical Issues", "Forgotten", "Other")
reasons_closed_project_table

```

```{r reasonopen} 
apa_table(reasons_open_project_table, digits = 0, caption = "Summary of main reasons researchers self-reported to open their OSF project page.")
```

```{r reasonclosed} 
apa_table(reasons_closed_project_table, digits = 0, caption = "Summary of main reasons researchers self-reported to not open their OSF project page.")
```

\newpage

# Motivations for opening or not opening OSF project pages

We were also interested in the motivation to either make the associated OSF project public or keep it private. While most researchers (79%) mentioned a motivation to practice open science as the primary reason for opening an OSF project (see Table \@ref(tab:reasonopen)), more diverse reasons were given for keeping the OSF project closed (see Table \@ref(tab:reasonclosed)). Many researchers (36%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was open. The second most common reason not to open the project (26%) was that researchers simply forgot to open the project. Others made the moment to open the project dependent on the publication of the study (14%), and technical issues (e.g., a lack of familiarity or misunderstanding about the OSF) were reasons to both open a project and to keep it private (in 8% and 10% of the cases, respectively).

# Researchers

Some researchers appeared in our database multiple times. This is an indication of the use of the OSF by early adopters in the years up to 2017. One author appeared three times, and 3 other researchers appeared 2 times. Although each registration can be published or not, there is the possibility of some dependencies in the dataset because the probability that these authors publish a paper might be correlated across registrations.

# References

<!-- # interlinepenalty prevents freak error when a hyperlink in reference breaks across a page -->
\begingroup
\interlinepenalty = 10000

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2023-05-21 supplement.tex
initial commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ,jou, a4paper,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Publication Bias; File-Drawer; Registry; Research Waste\newline\indent Word count: 1111}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
  pdfauthor={Eline Ensinck1 \& Daniël Lakens1},
  pdflang={en-EN},
  pdfkeywords={Publication Bias; File-Drawer; Registry; Research Waste},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
\author{Eline Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
\date{}

\shorttitle{SUPPLEMENT}

\authornote{

This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript, are available at \url{https://github.com/Lakens/xxx}.

Correspondence concerning this article should be addressed to Daniël Lakens, Den Dolech 1, 5600MB Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Eindhoven University of Technology}

\abstract{%
This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive preregistrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
}

\begin{document}
\maketitle

\hypertarget{details-on-classifying-registrations-as-a-research-study}{%
\section{Details on Classifying Registrations as a Research Study}\label{details-on-classifying-registrations-as-a-research-study}}

It can be challenging to determine whether a registration was performed with the goal to publish a study. Sometimes, the description of the preregistration or project page explicitly revealed that a registration was not an actual research study (for instance, when the group number of the course was shared), or it explicitly linked to a final publication. When it was not clear from the description on the OSF if the registration concerned an actual research study, we searched for information about the author(s) on the OSF. If the person who registered the project had various activity points and projects on the OSF, we assumed this person was an active researcher, and not a student. If someone had used the OSF at most a few times since 2017, and did not provide any personal information, we tried to determine if the user was a researcher by searching for scientific publications or membership of research groups (e.g.~profiles on institutional websites). If such information could be found, the registration was coded as an actual research study. If such information could not be found, the registration was marked as ``no research study'' (e.g., it was assumed to be a student assignment). In the case of multiple authors, it is possible that only a subgroup of the authors could be found. If only one of the authors seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF. However, if more than one author seemed to be an actual researcher, the registration was marked as an actual research study. These decisions necessarily introduce some arbitrariness in whether a study was intended to be published or not, and therefore we explored whether researchers intended to publish a study when we emailed researchers to follow up on unpublished registrations (see below).

We observed quite some variation in the amount of detail in the preregistrations that we examined. We therefore decided to code the `quality' of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the preregistrations in both groups and check for possible differences that could lead to different publication rates.

\hypertarget{details-on-classifying-studies-as-published-or-not}{%
\section{Details on Classifying Studies as Published or Not}\label{details-on-classifying-studies-as-published-or-not}}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:publicationtype}Type of object that matched the registration for all registrations that were publicly shared}

\begin{tabular}{llll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened} & \multicolumn{1}{c}{Total}\\
\midrule
Journal Article & 53 & 16 & 69\\
Preprint & 13 & 2 & 15\\
PhD Thesis & 6 & 7 & 13\\
Poster & 1 & 1 & 2\\
Report & 0 & 0 & 0\\
Conference Proceeding & 0 & 0 & 0\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

For each registration, we first searched for the combination of the title of the registration and the names of the authors in Google Scholar and examined the search results. We considered the registration published if it appeared as a journal article, preprint, PhD thesis in a repository, an online report, or conference proceedings. The frequency of each publication type is provided in Table \ref{tab:publicationtype}. When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the authors of the publication. We also searched the publication for a link to an OSF project page that was associated with the registration. If the publication indeed seemed to be about the same topic and was published after the registration date on the OSF, the study was marked as publicly shared.

Because titles of the registrations and papers often do not match we continued our search based on the names of the OSF users. For each user associated with a registration we retrieved a list of their publications and scanned through their publications after the registration date. If a paper similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine of the publication matched the registration. Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as ``not publicly shared''.

Our use of the term `published' differs from another inception cohort study in psychology (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}) who limited `publication' to journal articles and book chapters. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

When searching through the literature, different types of publications were found. To get an idea of the type of publications found within this sample, we distinguished between a journal article, preprint, PhD thesis, poster, draft/report, and conference paper. An overview is given in table xxx.

\hypertarget{extensiveness-of-the-details-in-registrations}{%
\section{Extensiveness of the details in registrations}\label{extensiveness-of-the-details-in-registrations}}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table-quality}Classification of the extensiveness of registrations.}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{1}{c}{Empty} & \multicolumn{1}{c}{Minimal} & \multicolumn{1}{c}{Short} & \multicolumn{1}{c}{Extensive}\\
\midrule
Manually Opened & 16 & 32 & 9 & 32\\
Automatically Opened & 13 & 23 & 6 & 39\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

Because of large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were. 18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration. At least a minimal description was given for 36\% of the registrations in the manually opened registrations and 28\% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in 10\% of the cases in the manually opened registrations and 7\% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (36\% and 48\% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \ref{tab:table-quality}. The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of details in the registrations (and thus that of the research studies) does not differ much between the two groups.

\hypertarget{fine-grained-categorization-of-reasons-for-non-publication}{%
\section{Fine-grained categorization of reasons for non-publication}\label{fine-grained-categorization-of-reasons-for-non-publication}}

In the main text we have classified the reasons provided by researchers not to publish in five categories. Below, we provide a more fine-grained classification consisting of 15 categories.

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:reasons_non_publish}Summary of main reasons researchers self-reported to not publish registered studies.}

\begin{tabular}{llll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened} & \multicolumn{1}{c}{Total}\\
\midrule
No significant results & 2 & 5 & 7\\
Left academia & 4 & 4 & 8\\
Paper rejected & 5 & 3 & 8\\
Failed replication & 1 & 3 & 4\\
Unfinished study & 1 & 5 & 6\\
Educational project & 0 & 0 & 0\\
Pilot & 0 & 1 & 1\\
Switched job / research directions & 0 & 3 & 3\\
Shared with funder (not the goal to publish) & 0 & 1 & 1\\
Lack of time / busy with other projects & 1 & 3 & 4\\
Conflicting / unclear results & 0 & 3 & 3\\
Flaws in procedure & 1 & 2 & 3\\
Still in progress & 1 & 1 & 2\\
Reviewers requested it & 1 & 2 & 3\\
Extra study (no priority) & 0 & 1 & 1\\
Health issues & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only the first or main reason was coded whenever respondents gave multiple reasons.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:reasonopen}Summary of main reasons researchers self-reported to open their OSF project page.}

\begin{tabular}{llll}
\toprule
 & \multicolumn{1}{c}{Open Science} & \multicolumn{1}{c}{Technical Issues} & \multicolumn{1}{c}{Other}\\
\midrule
Reasons & 18 & 2 & 3\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:reasonclosed}Summary of main reasons researchers self-reported to not open their OSF project page.}

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{Results} & \multicolumn{1}{c}{Publication Process} & \multicolumn{1}{c}{No New Information} & \multicolumn{1}{c}{Planning} & \multicolumn{1}{c}{Technical Issues} & \multicolumn{1}{c}{Forgotten} & \multicolumn{1}{c}{Other}\\
\midrule
Reasons & 1 & 6 & 15 & 4 & 4 & 11 & 2\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}

\newpage

\hypertarget{motivations-for-opening-or-not-opening-osf-project-pages}{%
\section{Motivations for opening or not opening OSF project pages}\label{motivations-for-opening-or-not-opening-osf-project-pages}}

We were also interested in the motivation to either make the associated OSF project public or keep it private. While most researchers (79\%) mentioned a motivation to practice open science as the primary reason for opening an OSF project (see Table \ref{tab:reasonopen}), more diverse reasons were given for keeping the OSF project closed (see Table \ref{tab:reasonclosed}). Many researchers (36\%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was open. The second most common reason not to open the project (26\%) was that researchers simply forgot to open the project. Others made the moment to open the project dependent on the publication of the study (14\%), and technical issues (e.g., a lack of familiarity or misunderstanding about the OSF) were reasons to both open a project and to keep it private (in 8\% and 10\% of the cases, respectively).

\hypertarget{researchers}{%
\section{Researchers}\label{researchers}}

Some researchers appeared in our database multiple times. This is an indication of the use of the OSF by early adopters in the years up to 2017. One author appeared three times, and 3 other researchers appeared 2 times. Although each registration can be published or not, there is the possibility of some dependencies in the dataset because the probability that these authors publish a paper might be correlated across registrations.

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup

\interlinepenalty = 10000

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-franco_publication_2014}{}}%
Franco, A., Malhotra, N., \& Simonovits, G. (2014). Publication bias in the social sciences: {Unlocking} the file drawer. \emph{Science}, \emph{345}(6203), 1502--1505. \url{https://doi.org/10.1126/SCIENCE.1255484}

\end{CSLReferences}

\endgroup

\end{document}

### 2023-05-21 analyze_prereg_api_data.R

@@ -1,0 +1,126 @@
+load("registration_data.RData")
+
+#1. Creating the dataframe through the OSF API
+# Lists of 3 elements
+head(registration_date_created)
+head(registration_id)
+head(project_id)
+
+library(httr)
+library(jsonlite)
+
+res_df <- data.frame(matrix(ncol = 19, nrow = length(registration_id)))
+
+for (project_i in 1:length(registration_id)){ # loop over all projects
+  # Start from the registration list we have.
+  # This retrieves a specific registration
+  id <- registration_id[project_i]
+  single_reg <- GET(paste("https://api.osf.io/v2/registrations/?filter[id]=",id, sep = ""))
+  registration <- fromJSON(rawToChar(single_reg$content))
+  reg_id <- registration$data$id
+  reg_date_created <- registration$data$attributes$date_created
+  reg_date_modified <- registration$data$attributes$date_modified
+  reg_date_registered <- registration$data$attributes$date_registered
+  category <- registration$data$attributes$category
+  description <- registration$data$attributes$description
+  fork <- registration$data$attributes$fork
+  public <- registration$data$attributes$public #must be true
+  reg_withdrawn <- registration$data$attributes$withdrawn
+  reg_withdrawal_justification <- registration$data$attributes$withdrawal_justification
+  has_project <- registration$data$attributes$has_project
+  parent_project <- registration$data$relationships$registered_from$data$id
+  # Get parent project
+  parent_node <- GET(paste(registration$data$relationships$registered_from$links$related$href))
+  project <- fromJSON(rawToChar(parent_node$content))
+  # If the parent project is closed we can not get the info below - stored as NA is not open
+  project_id <- ifelse(is.null(project$data$id), "NA", project$data$id)
+  web_address <- ifelse(is.null(project$data$links$html), "NA", project$data$links$html)
+  project_created <- ifelse(is.null(project$data$attributes$date_created), "NA", project$data$attributes$date_created)
+  project_modified <- ifelse(is.null(project$data$attributes$date_modified), "NA", project$data$attributes$date_modified)
+  project_title <- ifelse(is.null(project$data$attributes$title), "NA", project$data$attributes$title)
[…]

### 2023-05-21 get_data_from_osf_with_api.R

@@ -1,0 +1,43 @@
+########################################
+### Importing data from the OSF in R ###
+########################################
+
+install.packages(c("httr", "jsonlite"))
+
+library(httr)
+library(jsonlite)
+
+
+number_of_pages <- 1773            # total number of pages up to date_created 18-11-2017
+page_i <- 1                        # page index for the loop
+registration_id <- c()             # vector with all registration IDs (empty at this point)
+project_id <- c()                  # vector with all project IDs (empty at this point)
+res_temp <- c()                    # temporary vector used to store data in loop (empty at this point)
+registration_date_created <- c()   # vector with date_created of all registrations
+
+
+for (page_i in 1:number_of_pages)  # loop over all pages up to date_created 18-11-2017
+{
+  res <- GET(paste("https://api.osf.io/v2/registrations/?sort=date_created&page=", page_i, sep = "")) # access page i
+  registrations <- fromJSON(rawToChar(res$content))
+  res_temp <- registrations$data   # temporarily store data of current page
+  registration_id <- c(registration_id, res_temp$id) # add registration IDs of current page
+  registration_date_created <- c(registration_date_created, res_temp$attributes$date_created) # add date_created of these registrations
+  project_id <- c(project_id, res_temp$relationships$registered_from$data$id) # add project IDs of these registrations
+
+  page_i <- page_i+1               # update page index
+}
+
+print(registration_id)             # show registration IDs
+print(project_id)                  # show project IDs
+print(registration_date_created)   # show date_created of all registrations
+
+## Manually check date_registered > 4 years (first 17729 items)
+
+registration_id <- head(registration_id, -1)
+project_id <- head(project_id, -1)
+registration_date_created <- registration_date_created <- head(registration_date_created, -1)
+
+
+## Save relevant data
+save(registration_id, project_id, registration_date_created, file = "registration_data.RData")

### 2023-05-21 sampling_registrations.R

@@ -1,0 +1,21 @@
+##############################
+### Sampling registrations ###
+##############################
+
+## Load relevant data
+load("group1_and_2_IDs.RData")
+
+sample_size <- #... put here your sample size
+
+seed <- 100
+set.seed(seed)                # change seed to get different results when sampling again
+
+sample_group1 <- sample(group1_IDs, sample_size) # take a random sample of size "sample_size" from group 1
+sample_group2 <- sample(group2_IDs, sample_size) # take a random sample of size "sample_size" from group 2
+
+show(sample_group1)           # show all IDs sampled from group 1
+show(sample_group2)           # show all IDs sampled from group 2
+
+
+## Save samples from both groups
+save(group1_IDs, group2_IDs, file = "sample_group1_and_2_IDs.RData")

### 2023-05-21 sorting_registrations.R

@@ -1,0 +1,57 @@
+###########################################################################
+### Sorting registrations based on whether the project is public or not ###
+###########################################################################
+
+library(httr)
+library(jsonlite)
+
+## Load relevant data
+load("registration_data.RData")
+
+
+## Check whether projects are public or not
+
+project_public <- c()              # vector with booleans to store whether a project is public (true) or not (false)
+project_i <- 1                     # project index for the loop
+
+
+for (project_i in 1:length(project_id))           # loop over all projects
+{
+  res <- GET(paste("https://api.osf.io/v2/nodes/?filter[id]=", project_id[project_i], sep = "")) # access node (project) i
+  projects <- fromJSON(rawToChar(res$content))
+  if (projects$links$meta$total == 0) {           # in this case, the project is not public (in total, zero results)
+    project_public <- c(project_public, "false")
+  }
+  else {                                          # in this case, the project is public
+    project_public <- c(project_public, "true")
+  }
+  project_i <- project_i+1    # update project index
+}
+
+print(project_public)         # show whether projects are public (true) or not (false) in same order as IDs
+
+
+## Sort registrations based on whether the project is public or not
+
+group1_IDs <- c()             # vector with all registration IDs where the project is public
+group2_IDs <- c()             # vector with all registration IDs where the project is not public
+reg_i <- 1                    # registration index for the loop
+
+
+for (reg_i in 1:length(registration_id))          # loop over all registrations
+{
+  if (project_public[reg_i] == "true") {          # registration should be added to group 1
+    group1_IDs <- c(group1_IDs, registration_id[reg_i])
+  }
+  else {                                          # registration should be added to group 2
+    group2_IDs <- c(group2_IDs, registration_id[reg_i])
+  }
+  reg_i <- reg_i+1            # update registration index
+}
+
+print(group1_IDs)             # show all registrations where the project is public
+print(group2_IDs)             # show all registrations where the project is not public
+
+
+## Save IDs from both groups
+save(group1_IDs, group2_IDs, file = "group1_and_2_IDs.RData")

### 2023-05-21 paper.Rmd
update links

@@
   This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
-The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on .
+The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
 abstract: |

### 2023-05-21 paper.Rmd
checks and updates

@@
 Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published.
-For the whole population of registrations on the OSF before November 2017 we estimate 58% is published.
+For the whole population of registrations on the OSF before November 2017 we estimate 58% is published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
@@
 
-The practice of selective reporting has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@fanelli_positive_2010; @franco_publication_2014; @gerber_publication_2010].
+The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010].
 It is challenging to quantify how many studies remain unpublished.
 The most accurate estimates come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010].
-Dickersin and colleagues observed that from all 737 studies submitted to John Hopkins institutional review boards of the school of medicine and health 81% and 66% were published, respectively [@dickersin_factors_1992].
+Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81% and 66% were published [@dickersin_factors_1992].
 Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal.
-Of 293 clinical trials funded by NIH in 1979, 93% was published after a decade [@dickersin_nih_1993].
+Of 293 clinical trials funded by NIH in 1979 93% was published after a decade [@dickersin_nih_1993].
 In the only inception cohort study in the social sciences we know of, Franco et al.
@@
 However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013].
-The OSF offers researchers the possibility to voluntarily preregister their study by specifying their hypotheses, methods, and statistical analysis plan.
+The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.
 
-One interesting aspect of preregistrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ].
+One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ].
 This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago.
-It is therefore possible to use the database of preregistered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
+It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
 
@@
 First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years.
-Although this population of studies is not representative of all studies researchers perform, it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.
+Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.
 
@@
 As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
-Finally, while it is useful to quantify how many preregistered studies remain unpublished after four years, it is also important to understand why studies remain unpublished.
-The fourth aim of our study was to contacted the authors of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.
+Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is also important to understand why studies remain unpublished.
+The fourth aim of our study was to contacted the researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.
 
@@
 For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private.
-We randomly sampled registrations from both these groups.
+We sampled registrations from both these groups.
 During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database).
@@
 
-*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the preregistration was made public by the researchers, and 150 for which the preregistration was made public automatically after four years ).
+*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ).
 The OSF API does not provide information about how a project has been made public.
 To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted.
-We classified OSF preregistrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public.
+We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public.
 Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project.
@@
 
-*Classifying Publication Status*: Studies can be accessible in different degrees of accessibility, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021].
+*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021].
 We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results.
-In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis.
+In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail).
 We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies.
@@
 Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022].
-For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a preregistration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
+For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
 
@@
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
-Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` articles as unpublished, and for `r table(registration_data_included$published_before_email)[4]` articles we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
+Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
 
@@
 
-For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the authors.
+For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers.
 We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished.
-We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` authors with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*percentage_responded$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*percentage_responded$sum[2],2)`%) replied to our email with additional information to update our classification.
+We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` researchers with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*replies_per_group$sum[1]/contacted_researchers_per_group$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*replies_per_group$sum[2]/contacted_researchers_per_group$sum[2],2)`%) replied to our email with additional information to update our classification.
 We sent `r contacted_researchers_per_publication_status$sum[2]` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r responses_per_publication_status$sum[2]` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses).
-Two additional authors replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
+Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
 
@@
 After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%.
-Sometimes a publication we found in the literature did not belong to the preregistration.
-If the study associated with the registration was published in another article than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
+Sometimes a publication we found in the literature did not belong to the registration.
+If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
 In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found.
 For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.
-
 We received `r sum(match_per_classification[4,2:3])` responses for registrations we were uncertain about, and these follow-up emails indicated that `r match_per_classification[4,3]` (`r round(100*match_per_classification[4,3]/sum(match_per_classification[4,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.
@@
 In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published.
-Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their preregistration on the OSF.
+Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their registration on the OSF.
 
@@
                  )
+
+result_population <- binom.confint(x = estimated_nonpublication[3,6], n = (estimated_nonpublication[3,6]+estimated_nonpublication[3,7]), tol = 1e-8, method = "wilson")
+
 colnames(estimated_nonpublication) <- c("Group", "Registrations", "% Included", "Included", "% Published", "Published", "Not Published")
 apa_table(estimated_nonpublication, digits = 0, caption = "Estimated number of published and unpublished studies registered on the OSF before November 2017.")
+
 ```
@@
 After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]).
-This sample contained an almost equal number of manually opened and automatically opened registrations.
-As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations.
-Multiplying our publications estimates by the estimated number of research studies registered on the OSF before November 2017 we see `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished.
-Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100 * estimated_nonpublication[3,6] / (estimated_nonpublication[3,6] + estimated_nonpublication[3,7]),2)`% of registrations are published as an article, preprint, thesis, or poster after at least four years.
+Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations.
+As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
+Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished.
+Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
 
@@
 
-We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy, were classified as manually opened by the researchers have been published.
+We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
 In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
@@
 There can be many reasons why a researcher does not publish a performed study.
-We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the Supplementary Material).
+We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the online supplement).
 Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).
@@
 Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), waiting until a project was published (`r reasons_closed_project_table[2]` times), and technical issues (`r reasons_closed_project_table[5]` times).
-Finally, we were interested in how many researchers who preregistered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
+For more details, see the online supplement.
+Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
 Although not all of the email respondents answered this question, `r sum(registration_data$four_years_known == 1)` of the researchers indicated they were aware of this policy, and `r sum(registration_data$four_years_known == 0)` were not aware of this policy.
@@
 
-Our examination of `r sum(included_after$sum_after)` registration on the Open Science framework created before November 18, 2017, led to an estimated (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]) of registrations that were published.
+Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017.
 Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
@@
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around `r 100-round(100*result_total[4], 2)`% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
-Although not all unreported studies necessarily reflect research waste, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.
+The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
+Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.
 
-The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the results (e.g., null results or failed replications) were the reason that the study remained unpublished are concerning in light of the possibility that the absence of these studies contributed to publication bias in the scientific literature.
+The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished ia due to the results (e.g., null results or failed replications) is concerning.
+It is possible that the  absence of these studies contributes to publication bias in the scientific literature.
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014].
@@
 The practice to register studies is becoming more widespread, but up to 2017 was predominantly done by early adopters interested in open science practices.
-It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not preregister in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer.
+It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer.
 We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published.
@@
 The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large.
-At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, failed replications) play a role in many (if not all) scientific contexts.
+At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
 Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.

### 2023-05-21 paper.tex
update links
checks and updates

@@
 This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
-The computationally reproducible version of this manuscript, are available at \url{https://github.com/Lakens/xxx}.
+The computationally reproducible version of this manuscript is available at \url{https://github.com/Lakens/registered_published} and additional materials on \url{https://osf.io/8uqfb/}.
 
@@
 Examining 315 registrations revealed that 169 were research studies, of which 104 (62\%) were published.
-For the whole population of registrations on the OSF before November 2017 we estimate 58\% is published.
+For the whole population of registrations on the OSF before November 2017 we estimate 58\% is published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
@@
 
-The practice of selective reporting has been demonstrated in various disciplines, ranging from psychology and sociology to economics (\protect\hyperlink{ref-fanelli_positive_2010}{Fanelli, 2010}; \protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}).
+The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}).
 It is challenging to quantify how many studies remain unpublished.
 The most accurate estimates come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}).
-Dickersin and colleagues observed that from all 737 studies submitted to John Hopkins institutional review boards of the school of medicine and health 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}).
+Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81\% and 66\% were published (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}).
 Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal.
-Of 293 clinical trials funded by NIH in 1979, 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}).
+Of 293 clinical trials funded by NIH in 1979 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}).
 In the only inception cohort study in the social sciences we know of, Franco et al.~(2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
@@
 However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain (\protect\hyperlink{ref-spies_open_2013}{Spies, 2013}).
-The OSF offers researchers the possibility to voluntarily preregister their study by specifying their hypotheses, methods, and statistical analysis plan.
+The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.
 
-One interesting aspect of preregistrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) will be made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}.
+One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) will be made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}.
 This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago.
-It is therefore possible to use the database of preregistered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
+It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
 
@@
 For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project is private.
-We randomly sampled registrations from both these groups.
+We sampled registrations from both these groups.
 During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database).
@@
 
-\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the preregistration was made public by the researchers, and 150 for which the preregistration was made public automatically after four years ).
+\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ).
 The OSF API does not provide information about how a project has been made public.
 To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted.
-We classified OSF preregistrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public.
+We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public.
 Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project.
@@
 
-\emph{Classifying Publication Status}: Studies can be accessible in different degrees of accessibility, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
+\emph{Classifying Publication Status}: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
 We considered a study `published' if the study was communicated in any form that allows other researchers to learn about the results.
-In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis.
+In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail).
 We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies.
@@
 We therefore aimed to remove all registrations that were performed for practice purposes (e.g.~student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication).
-Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}).
-For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a preregistration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
+Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}).
+For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
 
@@
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
-Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 articles as unpublished, and for 30 articles we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
+Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 registrations as unpublished, and for 30 registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
 
-For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the authors.
+For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers.
 We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished.
-We contacted 109 researchers, 29 authors with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (26.61\%) and 53 (73.39\%) replied to our email with additional information to update our classification.
+We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification.
 We sent 1 email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received 1 response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses).
-Two additional authors replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
+Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
 
 After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%.
-Sometimes a publication we found in the literature did not belong to the preregistration.
-If the study associated with the registration was published in another article than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
+Sometimes a publication we found in the literature did not belong to the registration.
+If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
 In total, 48 of the 76 responses match with publications we found.
 For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.
-
 We received 25 responses for registrations we were uncertain about, and these follow-up emails indicated that 11 (44\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.
@@
 After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}).
-This sample contained an almost equal number of manually opened and automatically opened registrations.
-As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations.
-Multiplying our publications estimates by the estimated number of research studies registered on the OSF before November 2017 we see 5550 registrations are published, and 3994 remain unpublished.
-Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\% of registrations are published as an article, preprint, thesis, or poster after at least four years.
+Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations.
+As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
+Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that 5550 registrations are published, and 3994 remain unpublished.
+Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
 
@@
 
-We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy, were classified as manually opened by the researchers have been published.
+We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
 In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
@@
 There can be many reasons why a researcher does not publish a performed study.
-We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the Supplementary Material).
+We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the online supplement).
 Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).
@@
 Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (15 times), researchers forgot to open it (11 times), waiting until a project was published (6 times), and technical issues (4 times).
-Finally, we were interested in how many researchers who preregistered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
+For more details, see the online supplement.
+Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
 Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.
@@
 
-Our examination of 169 registration on the Open Science framework created before November 18, 2017, led to an estimated (61.25\%, 95\% CI {[}53.74; 68.27{]}) of registrations that were published.
+Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017.
 Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
@@
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around 38.75\% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
-Although not all unreported studies necessarily reflect research waste, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.
+The possibility that around 41.85\% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
+Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.
 
-The fact that for 20\% of unpublished studies researchers indicated that the results (e.g., null results or failed replications) were the reason that the study remained unpublished are concerning in light of the possibility that the absence of these studies contributed to publication bias in the scientific literature.
+The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished ia due to the results (e.g., null results or failed replications) is concerning.
+It is possible that the absence of these studies contributes to publication bias in the scientific literature.
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-fanelli_positive_2010}{}}%
-Fanelli, D. (2010). {``{Positive}''} {Results Increase Down} the {Hierarchy} of the {Sciences}. \emph{PLoS ONE}, \emph{5}(4). \url{https://doi.org/10.1371/journal.pone.0010068}
-
 \leavevmode\vadjust pre{\hypertarget{ref-franco_publication_2014}{}}%

### 2023-05-21 supplement.Rmd
update links
checks and updates

@@
   This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
-The computationally reproducible version of this manuscript, are available at https://github.com/Lakens/xxx.
+The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
 abstract: |
-  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive preregistrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
+  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
 
@@
 It can be challenging to determine whether a registration was performed with the goal to publish a study.
-Sometimes, the description of the preregistration or project page explicitly revealed that a registration was not an actual research study (for instance, when the group number of the course was shared), or it explicitly linked to a final publication.
-When it was not clear from the description on the OSF if the registration concerned an actual research study, we searched for information about the author(s) on the OSF.
+Sometimes, the description of the registration or project page explicitly revealed that a registration was not an actual research study (for instance, when the group number of the course was shared), or it explicitly linked to a final publication.
+When it was not clear from the description on the OSF if the registration concerned an actual research study, we searched for information about the researcher(s) on the OSF.
 If the person who registered the project had various activity points and projects on the OSF, we assumed this person was an active researcher, and not a student.
@@
 If such information could not be found, the registration was marked as “no research study” (e.g., it was assumed to be a student assignment).
-In the case of multiple authors, it is possible that only a subgroup of the authors could be found.
-If only one of the authors seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF.
-However, if more than one author seemed to be an actual researcher, the registration was marked as an actual research study.
+In the case of multiple researchers, it is possible that only a subgroup of the researchers could be found.
+If only one of the researchers seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF.
+However, if more than one researcher seemed to be an actual researcher, the registration was marked as an actual research study.
 These decisions necessarily introduce some arbitrariness in whether a study was intended to be published or not, and therefore we explored whether researchers intended to publish a study when we emailed researchers to follow up on unpublished registrations (see below).
 
-We observed quite some variation in the amount of detail in the preregistrations that we examined.
+We observed quite some variation in the amount of detail in the registrations that we examined.
 We therefore decided to code the ‘quality’ of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
@@
 If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4.
-In this way, we could compare the quality of the preregistrations in both groups and check for possible differences that could lead to different publication rates.
+In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.
 
@@
 
-For each registration, we first searched for the combination of the title of the registration and the names of the authors in Google Scholar and examined the search results.
+For each registration, we first searched for the combination of the title of the registration and the names of the researchers in Google Scholar and examined the search results.
 We considered the registration published if it appeared as a journal article, preprint, PhD thesis in a repository, an online report, or conference proceedings.
 The frequency of each publication type is provided in Table \@ref(tab:publicationtype).
-When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the authors of the publication.
+When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the researchers of the publication.
 We also searched the publication for a link to an OSF project page that was associated with the registration.
@@
 This is an indication of the use of the OSF by early adopters in the years up to 2017.
-One author appeared three times, and 3 other researchers appeared 2 times.
+One researcher appeared three times, and 3 other researchers appeared 2 times.
 Although each registration can be published or not, there is the possibility of some dependencies in the dataset because the probability that these authors publish a paper might be correlated across registrations.

### 2023-05-21 supplement.tex
update links
checks and updates

@@
 \abstract{%
-This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive preregistrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
+This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
 }
@@
 If such information could not be found, the registration was marked as ``no research study'' (e.g., it was assumed to be a student assignment).
-In the case of multiple authors, it is possible that only a subgroup of the authors could be found.
-If only one of the authors seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF.
-However, if more than one author seemed to be an actual researcher, the registration was marked as an actual research study.
+In the case of multiple researchers, it is possible that only a subgroup of the researchers could be found.
+If only one of the researchers seemed to be a real researcher, we assumed that the registration was part of a student project, where the researcher supervised the other users of the OSF.
+However, if more than one researcher seemed to be an actual researcher, the registration was marked as an actual research study.
 These decisions necessarily introduce some arbitrariness in whether a study was intended to be published or not, and therefore we explored whether researchers intended to publish a study when we emailed researchers to follow up on unpublished registrations (see below).
 
-We observed quite some variation in the amount of detail in the preregistrations that we examined.
+We observed quite some variation in the amount of detail in the registrations that we examined.
 We therefore decided to code the `quality' of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
@@
 
-For each registration, we first searched for the combination of the title of the registration and the names of the authors in Google Scholar and examined the search results.
+For each registration, we first searched for the combination of the title of the registration and the names of the researchers in Google Scholar and examined the search results.
 We considered the registration published if it appeared as a journal article, preprint, PhD thesis in a repository, an online report, or conference proceedings.
 The frequency of each publication type is provided in Table \ref{tab:publicationtype}.
-When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the authors of the publication.
+When a publication with a similar title was identified, the publication was downloaded and we determined if the publication matched the topic of the registration, was published after the registration date on the OSF, and the OSF users on the registration at least partly overlapped with the researchers of the publication.
 We also searched the publication for a link to an OSF project page that was associated with the registration.

### 2023-05-29 paper.Rmd
incoporating comments Eline

@@
 library(binom)
+library(xfun)
 
@@
 
-Scientists selectively publish studies they perform [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959].
+Not all studies scientists perform end up in the scientific literature [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959].
 Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions [@easterbrook_publication_1991; @lishner_sorting_2021].
-Research resources are wasted when studies that have the potential to contribute to scientific knowledge go unpublished, [@buxton_avoiding_2021; @chalmers_avoidable_2009].
+When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted [@buxton_avoiding_2021; @chalmers_avoidable_2009].
+The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010], but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer [@rosenthal_file_1979].
 
-The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010].
-It is challenging to quantify how many studies remain unpublished.
-The most accurate estimates come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010].
+The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010].
 Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81% and 66% were published [@dickersin_factors_1992].
@@
 In the only inception cohort study in the social sciences we know of, Franco et al.
-(2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
+[-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
 
@@
 First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years.
-Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.
+Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues [-@franco_publication_2014] as any researcher can register a study on the OSF.
 
 Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
-By examining the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
+By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
 This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
 
-Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not.
-For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study.
+Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not.
+For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished.
 As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
-Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is also important to understand why studies remain unpublished.
-The fourth aim of our study was to contacted the researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.
+
+Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished.
+The fourth aim of our study was to contact researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, ask why their study remains unpublished.
 
@@
 Registrations are part of at least one associated project page on the OSF.
-Researchers might still work on projects four years after a registration.
+Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample.
 The final classification was based on whether the projects were public in April 2022.
@@
 
-included_table <- cbind(included_before$sum_before, 100*included_before$mean, included_after$sum_after, 100*included_after$mean, included_after$n)
+included_table <- cbind(paste(included_before$sum_before, " (", sprintf("%1.2f%%", 100*included_before$mean), ")", sep = ""), paste(included_after$sum_after, " (",sprintf("%1.2f%%", 100*included_after$mean), ")", sep = ""))
 
 rownames(included_table) <- c(paste("Manually Opened (n = ", included_after$n[1], ")", sep = ""), paste("Automatically Opened (n = ", included_after$n[2], ")", sep = ""))
-colnames(included_table) <- c("Included Before Emails", "Percentage Before Emails", "Included After Emails", "Percentage After Emails", "Total")
+colnames(included_table) <- c("Included Before Emails", "Included After Emails")
 included_table
@@
 Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations.
-As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper.
-We therefore aimed to remove all registrations that were performed for practice purposes (e.g.
-student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication).
-Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022].
-For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
+Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish.
+We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g.
+student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022], and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
 
@@
 We originally included `r sum(included_before$sum_before)` registrations.
-After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, or being performed without the goal of publishing the data, our final sample size consists of `r sum(included_after$sum_after)` registrations, where for `r included_after$sum_after[1]` registrations the main project was public and for `r included_after$sum_after[2]` registrations the main project was not public.
+After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of `r sum(included_after$sum_after)` registrations, where for `r included_after$sum_after[1]` registrations the main project was public and for `r included_after$sum_after[2]` registrations the main project was not public.
 An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \@ref(tab:table-excluded).
@@
 ```{r table-included, echo = FALSE}
-apa_table(t(included_table), digits = 0, caption = "Studies included in the analysis before and after e-mailing researchers.", note = "The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.")
+apa_table(included_table, digits = 0, caption = "Studies included in the analysis before and after e-mailing researchers.")
 ```
@@
 ```{r table-excluded, echo = FALSE}
-apa_table(t(excl_table), digits = 0, caption = "Reasons studies were excluded from the analysis.")
+apa_table(t(excl_table), digits = 0, caption = "Reasons studies were excluded from the analysis.", note = "The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.")
 ```
@@
 We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` researchers with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*replies_per_group$sum[1]/contacted_researchers_per_group$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*replies_per_group$sum[2]/contacted_researchers_per_group$sum[2],2)`%) replied to our email with additional information to update our classification.
-We sent `r contacted_researchers_per_publication_status$sum[2]` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r responses_per_publication_status$sum[2]` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses).
+We sent `r numbers_to_words(contacted_researchers_per_publication_status$sum[2])` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r numbers_to_words(responses_per_publication_status$sum[2])` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses).
 Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
@@
 For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.
-We received `r sum(match_per_classification[4,2:3])` responses for registrations we were uncertain about, and these follow-up emails indicated that `r match_per_classification[4,3]` (`r round(100*match_per_classification[4,3]/sum(match_per_classification[4,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.
-
 Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped.
 For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found.
-Of the `r match_per_classification[4,2]` cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
+Of the `r match_per_classification[4,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
 In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published.
-Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their registration on the OSF.
+Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.
 
@@
 Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published.
-The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published studies.
+The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies.
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
@@
 As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
-Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished.
+Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished.
 Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
@@
 Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
-In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
+In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
 
@@
 We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the online supplement).
-Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).
+Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).
 
@@
 
-When asked why researchers made their OSF project page open, most researchers (`r reasons_open_project_table[2]` out of `r sum(reasons_open_project_table)` mentioned a motivation to practice open science.
-Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), waiting until a project was published (`r reasons_closed_project_table[2]` times), and technical issues (`r reasons_closed_project_table[5]` times).
+When asked why researchers made their OSF project page open, most researchers (`r reasons_open_project_table[1]` out of `r sum(reasons_open_project_table)`) mentioned a motivation to practice open science.
+Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), were waiting until a project was published (`r reasons_closed_project_table[2]` times), or experienced technical issues (`r reasons_closed_project_table[5]` times).
 For more details, see the online supplement.
@@
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
+The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
 Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.
 
-The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished ia due to the results (e.g., null results or failed replications) is concerning.
+The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017].
 It is possible that the  absence of these studies contributes to publication bias in the scientific literature.
@@
 If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent.
-With the rise of data repositories and preprints it has become feasible and easy to share the results of studies, although future work that makes it easier to find, evaluate, and integrate study results is important.
+With the rise of data repositories and preprints it has become feasible and easy to share the results of studies.
 
@@
 Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017.
-The practice to register studies is becoming more widespread, but up to 2017 was predominantly done by early adopters interested in open science practices.
+Users of the OSF in these years are early adopters interested in open science practices.
 It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer.
 We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published.
-Registering a study requires work, and it possible that researchers only register studies they feel have a higher probability of being submitted for publication.
+Registering a study requires work, and it is possible that researchers only register studies they feel have a higher probability of being submitted for publication.
 Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines.
-The probability that researchers have the time to share data from a registered study might change over time, and could for example be in recent years due to the COVID pandemic.
+The probability that researchers have the time to share data from a registered study might change over time, and could be higher due to the COVID pandemic.
 In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.
@@
 Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
-In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be few unpublished studies.
+In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, so there might be few unpublished studies.
 In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample.
@@
 *Recommendations for Registries*.
-We found that registrations are sometimes used to create a stable repository after a study has been completed, and sometimes to register the existence (and sometimes methodological details) of a planned study.
-To be able to distinguish these to uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘prospective registration’ or ‘preregistration’ from ‘post registration’ or ‘data archiving’).
+We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed.
+To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘prospective registration’ or ‘preregistration’ from ‘post registration’ or ‘data archiving’).
 A third registration option should be created for all registrations that are done for purely educational or practice purposes.
@@
 If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the “Other comments” field.
-It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration [@akker_effectiveness_2023] and to create machine-readable analysis code that describe when statistical hypotheses are corroborated or falsified [@lakens_improving_2021].
+It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration [@akker_effectiveness_2023] and to create machine-readable analysis code that describes when statistical hypotheses are corroborated or falsified [@lakens_improving_2021].
 Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed.

### 2023-05-29 paper.tex
incoporating comments Eline

@@
 
-Scientists selectively publish studies they perform (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}).
+Not all studies scientists perform end up in the scientific literature (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}).
 Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions (\protect\hyperlink{ref-easterbrook_publication_1991}{Easterbrook, Berlin, Gopalan, \& Matthews, 1991}; \protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
-Research resources are wasted when studies that have the potential to contribute to scientific knowledge go unpublished, (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).
+When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).
+The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}), but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer (\protect\hyperlink{ref-rosenthal_file_1979}{Rosenthal, 1979}).
 
-The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}).
-It is challenging to quantify how many studies remain unpublished.
-The most accurate estimates come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}).
+The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}).
 Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81\% and 66\% were published (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}).
@@
 Of 293 clinical trials funded by NIH in 1979 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}).
-In the only inception cohort study in the social sciences we know of, Franco et al.~(2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
+In the only inception cohort study in the social sciences we know of, Franco et al.
+(\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
 
@@
 First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years.
-Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.
+Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (\protect\hyperlink{ref-franco_publication_2014}{2014}) as any researcher can register a study on the OSF.
 
 Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
-By examining the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
+By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
 This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
 
-Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not.
-For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study.
+Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not.
+For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished.
 As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
-Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is also important to understand why studies remain unpublished.
-The fourth aim of our study was to contacted the researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.
+
+Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished.
+The fourth aim of our study was to contact researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, ask why their study remains unpublished.
 
@@
 Of these, the associated project was public for 164 registrations and the associated project was closed for 151 registrations.
-As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper.
-We therefore aimed to remove all registrations that were performed for practice purposes (e.g.~student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication).
-Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}).
-For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.
+Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish.
+We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g.~student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}), and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
 
@@
 We originally included 176 registrations.
-After excluding 7 registrations based on email responses for being student projects, or being performed without the goal of publishing the data, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public.
+After excluding 7 registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public.
 An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \ref{tab:table-excluded}.
@@
 \toprule
- & \multicolumn{1}{c}{Manually Opened (n = 164)} & \multicolumn{1}{c}{Automatically Opened (n = 151)}\\
+ & \multicolumn{1}{c}{Included Before Emails} & \multicolumn{1}{c}{Included After Emails}\\
 \midrule
-Included Before Emails & 90 & 86\\
-Percentage Before Emails & 55 & 57\\
-Included After Emails & 88 & 81\\
-Percentage After Emails & 54 & 54\\
-Total & 164 & 151\\
+Manually Opened (n = 164) & 90 (54.88\%) & 88 (53.66\%)\\
+Automatically Opened (n = 151) & 86 (56.95\%) & 81 (53.64\%)\\
 \bottomrule
-\addlinespace
 \end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.}
-\end{tablenotes}
 
@@
 \bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The sum is greater than the total number of excluded registrations because an individual registration can be excluded for multiple reasons.}
+\end{tablenotes}
 
@@
 We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification.
-We sent 1 email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received 1 response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses).
+We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses).
 Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
@@
 For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.
-We received 25 responses for registrations we were uncertain about, and these follow-up emails indicated that 11 (44\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.
-
 Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped.
 For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found.
-Of the 14 cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
+Of the 14 (28\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
 In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published.
-Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their registration on the OSF.
+Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.
 
 Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published.
-The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published studies.
+The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies.
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
@@
 As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
-Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that 5550 registrations are published, and 3994 remain unpublished.
+Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that 5550 registrations are published, and 3994 remain unpublished.
 Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
@@
 Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
-In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
+In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
 
@@
 We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the online supplement).
-Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).
+Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).
 
@@
 
-When asked why researchers made their OSF project page open, most researchers (2 out of 23 mentioned a motivation to practice open science.
-Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (15 times), researchers forgot to open it (11 times), waiting until a project was published (6 times), and technical issues (4 times).
+When asked why researchers made their OSF project page open, most researchers (18 out of 23) mentioned a motivation to practice open science.
+Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), were waiting until a project was published (6 times), or experienced technical issues (4 times).
 For more details, see the online supplement.
@@
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around 41.85\% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research.
+The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
 Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.
 
-The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished ia due to the results (e.g., null results or failed replications) is concerning.
+The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}).
 It is possible that the absence of these studies contributes to publication bias in the scientific literature.
@@
 \emph{Recommendations for Registries}.
-We found that registrations are sometimes used to create a stable repository after a study has been completed, and sometimes to register the existence (and sometimes methodological details) of a planned study.
-To be able to distinguish these to uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving').
+We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed.
+To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving').
 A third registration option should be created for all registrations that are done for purely educational or practice purposes.
@@
 If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the ``Other comments'' field.
-It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration (\protect\hyperlink{ref-akker_effectiveness_2023}{Akker et al., 2023}) and to create machine-readable analysis code that describe when statistical hypotheses are corroborated or falsified (\protect\hyperlink{ref-lakens_improving_2021}{Lakens \& DeBruine, 2021}).
+It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration (\protect\hyperlink{ref-akker_effectiveness_2023}{Akker et al., 2023}) and to create machine-readable analysis code that describes when statistical hypotheses are corroborated or falsified (\protect\hyperlink{ref-lakens_improving_2021}{Lakens \& DeBruine, 2021}).
 Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed.
@@
 Bernal, J. D. (1939). \emph{The {Social Function Of Science}}. {London}: {Routledge}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bottesini_what_2022}{}}%
+Bottesini, J.
+G., Rhemtulla, M., \& Vazire, S.
+(2022).
+What do participants think of our research practices?
+{An} examination of behavioural psychology participants' preferences.
+\emph{Royal Society Open Science}, \emph{9}(4), 200048.
+\url{https://doi.org/10.1098/rsos.200048}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pickett_questionable_2017}{}}%
+Pickett, J.
+T., \& Roche, S.
+P.
+(2017).
+Questionable, {Objectionable} or {Criminal}?
+{Public Opinion} on {Data Fraud} and {Selective Reporting} in {Science}.
+\emph{Science and Engineering Ethics}, 1--21.
+\url{https://doi.org/10.1007/s11948-017-9886-2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rosenthal_file_1979}{}}%
+Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638.
+
 \leavevmode\vadjust pre{\hypertarget{ref-scheel_excess_2021}{}}%

### 2023-05-29 paper.Rmd
incorporating all comments

@@
 The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
+We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft.
 abstract: |
-  We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared.
-Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published.
-For the whole population of registrations on the OSF before November 2017 we estimate 58% is published within at least 4 years.
+  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared.
+Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published.
+We estimate that 5550 out of 9544 (58%) of registrations on the OSF are published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
-It is often challenging to identify whether public registrations are published due to a lack of information in registrations.
-In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
-Our project shows a substantial amount of data that researchers collect is never publicly shared.
-Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature.
-Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published.
-The OSF has a policy to make all registrations public after four years.
-This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years.
-A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.
+In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
+Our study shows that a substantial amount of data that researchers collect is never publicly shared.
 
-keywords          : "Publication Bias; File-Drawer; Registry; Research Waste"
-wordcount         : "1111"
+keywords          : "File Drawer; Registries; Research Waste; Scientific Publication"
+wordcount         : "4501"
 bibliography      : ["RegistriesPublication.bib"]
@@
 
-Not all studies scientists perform end up in the scientific literature [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959].
+Not all studies that scientists perform end up in the scientific literature [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959].
 Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions [@easterbrook_publication_1991; @lishner_sorting_2021].
-When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted [@buxton_avoiding_2021; @chalmers_avoidable_2009].
-The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010], but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer [@rosenthal_file_1979].
+When studies that have the potential to contribute to scientific knowledge go unpublished research resources are wasted [@buxton_avoiding_2021; @chalmers_avoidable_2009].
+Although it is challenging to quantify how many studies remain unpublished the existence of the proverbial file drawer [@rosenthal_file_1979] has been demonstrated in disciplines such as psychology, sociology, economics, and medicine [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010; @dickersin_factors_1992].
 
 The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010].
-Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81% and 66% were published [@dickersin_factors_1992].
-Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal.
-Of 293 clinical trials funded by NIH in 1979 93% was published after a decade [@dickersin_nih_1993].
-In the only inception cohort study in the social sciences we know of, Franco et al.
-[-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
+For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992].
+In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
 
-One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database.
-An example of such a study registry is ClinicalTrials.gov [@dickersin_evolution_2012].
+One way to make all studies that have been performed known to peers is to require researchers to (pre)register their study in a publicly accessible database [@dickersin_evolution_2012].
+Registries often require researchers to update a registered study with the results.
+An example of such a study registry is ClinicalTrials.gov.
 The requirement to register certain types of studies does not exist in psychology.
@@
 First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years.
-Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues [-@franco_publication_2014] as any researcher can register a study on the OSF.
+Although registered studies are only a subset of all studies researchers perform, in the results section we estimate that our findings apply to 9,544 research studies registered on the OSF up to November 2017.
 
 Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
-By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
-This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
+By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions.
+How often do researchers voluntarily share information about their study, even when the study remains unpublished?
+And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?
+Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
 
@@
 Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished.
-The fourth aim of our study was to contact researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, ask why their study remains unpublished.
+The fourth aim of our study was to contact researchers of registrations of studies that were not published and ask why their study remains unpublished.
 
@@
 
-*Data sources*: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API).
+*Data sources*: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study).
 Registrations are part of at least one associated project page on the OSF.
@@
 The final classification was based on whether the projects were public in April 2022.
-For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private.
-We sampled registrations from both these groups.
+For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project was private.
+We randomly sampled registrations from both these groups.
 During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database).
-Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.
+Our sampling strategy increased the probability that studies with multiple registrations were included in the study.
 
@@
 We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies.
-This use of the term ‘published’ differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles.
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.
+Our definition of ‘published’ is broader than in previous inception cohort studies (e.g., @dickersin_factors_1992; @franco_publication_2014).
+We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
 
@@
 
-*Inclusion criteria*: After some projects were reclassified during the data analysis in total `r sum(included_after$n)` randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study.
+*Inclusion criteria*: In total `r sum(included_after$n)` randomly chosen registrations from manually and automatically opened registrations were examined to see whether they met the selection criteria of our study.
 Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations.
 Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish.
-We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g.
-student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022], and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
+We therefore coded and excluded registrations that were (1) withdrawn (e.g., all content is removed because an error was made in the registration, but the meta-data continues to exist), (2) performed for practice purposes (e.g.
+student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are unlikely to end up in the file drawer such as (4) Registered Reports, [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022], and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
 
@@
 We originally included `r sum(included_before$sum_before)` registrations.
-After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of `r sum(included_after$sum_after)` registrations, where for `r included_after$sum_after[1]` registrations the main project was public and for `r included_after$sum_after[2]` registrations the main project was not public.
+After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of `r sum(included_after$sum_after)` registrations.
+Of these, `r included_after$sum_after[1]` registrations were categorized as manually opened and `r included_after$sum_after[2]` registrations were categorized as automatically opened.
 An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \@ref(tab:table-excluded).
@@
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
-Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
+Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published.
+We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.
 
@@
 
-reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(results = sum(reason_if_unpublished == 1 | reason_if_unpublished == 4 | reason_if_unpublished == 11), review = sum(reason_if_unpublished == 3 | reason_if_unpublished == 14), not_goal_to_publish = sum(reason_if_unpublished == 6 | reason_if_unpublished == 7 | reason_if_unpublished == 9), planning = sum(reason_if_unpublished == 2 | reason_if_unpublished == 5 | reason_if_unpublished == 8 | reason_if_unpublished == 10 | reason_if_unpublished == 13 | reason_if_unpublished == 15 | reason_if_unpublished == 16), study_design = sum(reason_if_unpublished == 12))
+reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(planning = sum(reason_if_unpublished == 2 | reason_if_unpublished == 5 | reason_if_unpublished == 8 | reason_if_unpublished == 10 | reason_if_unpublished == 13 | reason_if_unpublished == 15 | reason_if_unpublished == 16), results = sum(reason_if_unpublished == 1 | reason_if_unpublished == 4 | reason_if_unpublished == 11), review = sum(reason_if_unpublished == 3 | reason_if_unpublished == 14), study_design = sum(reason_if_unpublished == 12), not_goal_to_publish = sum(reason_if_unpublished == 6 | reason_if_unpublished == 7 | reason_if_unpublished == 9))
 reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
@@
 rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
-colnames(reasons_table) <- c("Results", "Peer Review", "Not Goal to Publish", "Planning", "Study Design")
+colnames(reasons_table) <- c("Logistical Issues", "Results", "Peer Review", "Study Design", "Not Goal to Publish")
 
@@
 We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the online supplement).
-Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).
+Researchers indicated that their motivation to not publish was based on (1) logistical issues, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100*reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,2]/sum(reasons_table[3,]),0)`%), (3) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) problems with the study design, such as not reaching the intended sample size, or a statistical artifact (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).
 
-According to the responses we received, issues related to ‘planning’ are the biggest cause of unpublished studies in our sample.
+According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample.
 Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities.
@@
 rownames(reasons_closed_project_table) <- c("Reasons")
-colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Planning", "Technical Issues", "Forgotten", "Other")
+colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Logistical Issues", "Technical Issues", "Forgotten", "Other")
 reasons_closed_project_table
@@
 Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
-The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job.
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
@@
 
+The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job.
+Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues.
 The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017].
@@
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014].
-Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results [@allen_open_2019; @scheel_excess_2021].
-If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent.
-With the rise of data repositories and preprints it has become feasible and easy to share the results of studies.
+If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature [@schmidt_shall_2009], and if null-results remain unreported effect size estimates in meta-analyses will be inflated [@egger_bias_1997].
 
-It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study.
-First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report.
-Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017.
-Users of the OSF in these years are early adopters interested in open science practices.
-It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer.
-We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published.
-Registering a study requires work, and it is possible that researchers only register studies they feel have a higher probability of being submitted for publication.
-Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines.
-The probability that researchers have the time to share data from a registered study might change over time, and could be higher due to the COVID pandemic.
-In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.
+Our estimate has remaining uncertainty as some registrations for which authors did not respond to our email might be classified incorrectly.
+Furthermore, the estimate is specific to the context of our study, which were all registrations on the OSF created before November 18, 2017.
+Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF.
+Our estimate might not generalize to non-registered studies.
+The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic).
+In short, the exact percentage of studies that remain unpublished will be different in other contexts.
 
-However, our goal was not to establish a generalizable estimate.
-The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large.
-At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
-Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
-In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, so there might be few unpublished studies.
-In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample.
-Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.
+At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
+In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
+Our study demonstrates that the percentage of unpublished studies can be high.
+The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
+Empirically examining the size of the file drawer can determine if there is room for improvement.
 
 *Recommendations for Registries*.
-We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed.
-To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘prospective registration’ or ‘preregistration’ from ‘post registration’ or ‘data archiving’).
-A third registration option should be created for all registrations that are done for purely educational or practice purposes.
-The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money.
-It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years.
+We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed.
+To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘preregistration’ from ‘data archiving’).
+Allowing users to distinguish educational projects from research projects might also be useful.
+It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF.
 Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations.
-It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations.
-Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.
+It would be clearer if one could identify when registrations of components are part of the registration of the overarching project.
 
@@
 A substantial amount of data that researchers collect is never publicly shared.
-Every system will have some inefficiencies, and it is difficult to judge whether the percentage of unpublished data we observed in our sample is too high.
-What is perhaps most surprising is that researchers rarely talk about how many datasets they have collected that could have value for peers but that nevertheless linger in their filedrawer.
-Researchers might not feel like they can frankly discuss this topic due to the association of unpublished studies with publication bias.
-Although we found publication bias to be one reason to not share data, logistical issues were more commonly provided as a reason not to share data.
-More transparency about unpublished datasets would allow our field to learn and improve the way we work, and improve practices to increase the efficiency of psychological science.
+Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large [@dickersin_factors_1992].
+What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer.
+Researchers might feel uneasy to honestly discuss this topic because unpublished studies are strongly associated with bias.
+More transparency about unpublished studies would allow our field to improve the way we work and increase the efficiency of psychological science.
 

### 2023-05-29 paper.tex
incorporating all comments

@@
 {}{\PatchFailed}
-\keywords{Publication Bias; File-Drawer; Registry; Research Waste\newline\indent Word count: 1111}
+\keywords{File Drawer; Registries; Research Waste; Scientific Publication\newline\indent Word count: 4501}
 \usepackage{dblfloatfix}
@@
   pdflang={en-EN},
-  pdfkeywords={Publication Bias; File-Drawer; Registry; Research Waste},
+  pdfkeywords={File Drawer; Registries; Research Waste; Scientific Publication},
   hidelinks,
@@
 The computationally reproducible version of this manuscript is available at \url{https://github.com/Lakens/registered_published} and additional materials on \url{https://osf.io/8uqfb/}.
+We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft.
 
@@
 \abstract{%
-We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared.
-Examining 315 registrations revealed that 169 were research studies, of which 104 (62\%) were published.
-For the whole population of registrations on the OSF before November 2017 we estimate 58\% is published within at least 4 years.
+We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared.
+Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published.
+We estimate that 5550 out of 9544 (58\%) of registrations on the OSF are published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
-It is often challenging to identify whether public registrations are published due to a lack of information in registrations.
-In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
-Our project shows a substantial amount of data that researchers collect is never publicly shared.
-Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature.
-Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published.
-The OSF has a policy to make all registrations public after four years.
-This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years.
-A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.
+In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
+Our study shows that a substantial amount of data that researchers collect is never publicly shared.
 }
@@
 
-Not all studies scientists perform end up in the scientific literature (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}).
+Not all studies that scientists perform end up in the scientific literature (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}).
 Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions (\protect\hyperlink{ref-easterbrook_publication_1991}{Easterbrook, Berlin, Gopalan, \& Matthews, 1991}; \protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
-When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).
-The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}), but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer (\protect\hyperlink{ref-rosenthal_file_1979}{Rosenthal, 1979}).
+When studies that have the potential to contribute to scientific knowledge go unpublished research resources are wasted (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).
+Although it is challenging to quantify how many studies remain unpublished the existence of the proverbial file drawer (\protect\hyperlink{ref-rosenthal_file_1979}{Rosenthal, 1979}) has been demonstrated in disciplines such as psychology, sociology, economics, and medicine (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}; \protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}).
 
 The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}).
-Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81\% and 66\% were published (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}).
-Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal.
-Of 293 clinical trials funded by NIH in 1979 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}).
-In the only inception cohort study in the social sciences we know of, Franco et al.
-(\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
+For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}).
+In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
 
-One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database.
-An example of such a study registry is ClinicalTrials.gov (\protect\hyperlink{ref-dickersin_evolution_2012}{Dickersin \& Rennie, 2012}).
+One way to make all studies that have been performed known to peers is to require researchers to (pre)register their study in a publicly accessible database (\protect\hyperlink{ref-dickersin_evolution_2012}{Dickersin \& Rennie, 2012}).
+Registries often require researchers to update a registered study with the results.
+An example of such a study registry is ClinicalTrials.gov.
 The requirement to register certain types of studies does not exist in psychology.
@@
 First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years.
-Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (\protect\hyperlink{ref-franco_publication_2014}{2014}) as any researcher can register a study on the OSF.
+Although registered studies are only a subset of all studies researchers perform, in the results section we estimate that our findings apply to 9,544 research studies registered on the OSF up to November 2017.
 
 Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
-By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable.
-This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
+By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions.
+How often do researchers voluntarily share information about their study, even when the study remains unpublished?
+And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?
+Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
 
@@
 
-\emph{Data sources}: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API).
+\emph{Data sources}: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study).
 Registrations are part of at least one associated project page on the OSF.
@@
 The final classification was based on whether the projects were public in April 2022.
-For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project is private.
-We sampled registrations from both these groups.
+For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project was private.
+We randomly sampled registrations from both these groups.
 During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database).
-Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.
+Our sampling strategy increased the probability that studies with multiple registrations were included in the study.
 
@@
 We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies.
-This use of the term `published' differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles.
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.
+Our definition of `published' is broader than in previous inception cohort studies (e.g., Dickersin et al.
+(\protect\hyperlink{ref-dickersin_factors_1992}{1992}); Franco et al.
+(\protect\hyperlink{ref-franco_publication_2014}{2014})).
+We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
 
@@
 
-\emph{Inclusion criteria}: After some projects were reclassified during the data analysis in total 315 randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study.
+\emph{Inclusion criteria}: In total 315 randomly chosen registrations from manually and automatically opened registrations were examined to see whether they met the selection criteria of our study.
 Of these, the associated project was public for 164 registrations and the associated project was closed for 151 registrations.
 Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish.
-We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g.~student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}), and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
+We therefore coded and excluded registrations that were (1) withdrawn (e.g., all content is removed because an error was made in the registration, but the meta-data continues to exist), (2) performed for practice purposes (e.g.~student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are unlikely to end up in the file drawer such as (4) Registered Reports, (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}), and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).
 
@@
 We originally included 176 registrations.
-After excluding 7 registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public.
+After excluding 7 registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of 169 registrations.
+Of these, 88 registrations were categorized as manually opened and 81 registrations were categorized as automatically opened.
 An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \ref{tab:table-excluded}.
@@
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
-Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 registrations as unpublished, and for 30 registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.
+Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 registrations as unpublished, and for 30 registrations we were uncertain about whether the registration was published.
+We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.
 
@@
 We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the online supplement).
-Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).
+Researchers indicated that their motivation to not publish was based on (1) logistical issues, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), (2) the results of the study, such as null or unclear results and failed replications (25\%), (3) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (20\%), (4) problems with the study design, such as not reaching the intended sample size, or a statistical artifact (5\%), and (5) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%).
 
-According to the responses we received, issues related to `planning' are the biggest cause of unpublished studies in our sample.
+According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample.
 Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities.
@@
 \midrule
+Logistical Issues & 7 & 18 & 25\\
 Results & 3 & 11 & 14\\
 Peer Review & 6 & 5 & 11\\
+Study Design & 1 & 2 & 3\\
 Not Goal to Publish & 0 & 2 & 2\\
-Planning & 7 & 18 & 25\\
-Study Design & 1 & 2 & 3\\
 \bottomrule
@@
 Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
-The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job.
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
@@
 
-The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}).
+The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job.
+Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues.
+The fact that for 25\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}).
 It is possible that the absence of these studies contributes to publication bias in the scientific literature.
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}).
-Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}).
-If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent.
-With the rise of data repositories and preprints it has become feasible and easy to share the results of studies.
+If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature (\protect\hyperlink{ref-schmidt_shall_2009}{Schmidt, 2009}), and if null-results remain unreported effect size estimates in meta-analyses will be inflated (\protect\hyperlink{ref-egger_bias_1997}{Egger, Davey Smith, Schneider, \& Minder, 1997}).
 
-It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study.
-First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report.
-Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017.
-Users of the OSF in these years are early adopters interested in open science practices.
-It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer.
-We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published.
-Registering a study requires work, and it is possible that researchers only register studies they feel have a higher probability of being submitted for publication.
-Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines.
-The probability that researchers have the time to share data from a registered study might change over time, and could be higher due to the COVID pandemic.
-In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.
+Our estimate has remaining uncertainty as some registrations for which authors did not respond to our email might be classified incorrectly.
+Furthermore, the estimate is specific to the context of our study, which were all registrations on the OSF created before November 18, 2017.
+Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF.
+Our estimate might not generalize to non-registered studies.
+The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic).
+In short, the exact percentage of studies that remain unpublished will be different in other contexts.
 
-However, our goal was not to establish a generalizable estimate.
-The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large.
-At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
-Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
-In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, so there might be few unpublished studies.
-In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample.
-Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.
+At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
+In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
+Our study demonstrates that the percentage of unpublished studies can be high.
+The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
+Empirically examining the size of the file drawer can determine if there is room for improvement.
 
 \emph{Recommendations for Registries}.
-We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed.
-To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving').
-A third registration option should be created for all registrations that are done for purely educational or practice purposes.
-The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money.
-It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years.
+We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed.
+To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `preregistration' from `data archiving').
+Allowing users to distinguish educational projects from research projects might also be useful.
+It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF.
 Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations.
-It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations.
-Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.
+It would be clearer if one could identify when registrations of components are part of the registration of the overarching project.
 
@@
 A substantial amount of data that researchers collect is never publicly shared.
-Every system will have some inefficiencies, and it is difficult to judge whether the percentage of unpublished data we observed in our sample is too high.
-What is perhaps most surprising is that researchers rarely talk about how many datasets they have collected that could have value for peers but that nevertheless linger in their filedrawer.
-Researchers might not feel like they can frankly discuss this topic due to the association of unpublished studies with publication bias.
-Although we found publication bias to be one reason to not share data, logistical issues were more commonly provided as a reason not to share data.
-More transparency about unpublished datasets would allow our field to learn and improve the way we work, and improve practices to increase the efficiency of psychological science.
+Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}).
+What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer.
+Researchers might feel uneasy to honestly discuss this topic because unpublished studies are strongly associated with bias.
+More transparency about unpublished studies would allow our field to improve the way we work and increase the efficiency of psychological science.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dickersin_nih_1993}{}}%
-Dickersin, K., \& Min, Y.
-I.
-(1993).
-\href{https://www.ncbi.nlm.nih.gov/pubmed/8306005}{{NIH} clinical trials and publication bias}.
-\emph{The Online Journal of Current Clinical Trials}, \emph{Doc No 50}, {[}4967 words; 53 paragraphs{]}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-dickersin_factors_1992}{}}%
@@
 \url{https://doi.org/10.1016/0140-6736(91)90201-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-egger_bias_1997}{}}%
+Egger, M., Davey Smith, G., Schneider, M., \& Minder, C.
+(1997).
+Bias in meta-analysis detected by a simple, graphical test.
+\emph{BMJ (Clinical Research Ed.)}, \emph{315}(7109), 629--634.
+\url{https://doi.org/10.1136/bmj.315.7109.629}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-schmidt_shall_2009}{}}%
+Schmidt, S.
+(2009).
+Shall we really do it again?
+{The} powerful concept of replication is neglected in the social sciences.
+\emph{Review of General Psychology}, \emph{13}(2), 90--100.
+\url{https://doi.org/10.1037/a0015108}
+
 \leavevmode\vadjust pre{\hypertarget{ref-song_dissemination_2010}{}}%

### 2023-05-29 supplement.Rmd
updates supplement

@@
 
-keywords          : "Publication Bias; File-Drawer; Registry; Research Waste"
-wordcount         : "1111"
-bibliography      : ["RegistriesPublication.bib"]
 floatsintext      : yes
@@
 These decisions necessarily introduce some arbitrariness in whether a study was intended to be published or not, and therefore we explored whether researchers intended to publish a study when we emailed researchers to follow up on unpublished registrations (see below).
+As we did not email researchers when we felt confident the registration was not a research study, and as we did not receive replies from all researchers we emailed, the final classification has remaining uncertainty (see the discussion).
 
@@
 
-apa_table(t(publicationtype), digits = 0, caption = "Type of object that matched the registration for all registrations that were publicly shared")
+apa_table(t(publicationtype), digits = 0, caption = "Type of document that matched the registration for all registrations that were publicly shared")
 
@@
 For each user associated with a registration we retrieved a list of their publications and scanned through their publications after the registration date.
-If a paper similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine of the publication matched the registration.
-Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as “not publicly shared”.
-
-Our use of the term ‘published’ differs from another inception cohort study in psychology [@franco_publication_2014] who limited 'publication' to journal articles and book chapters.
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.
-
-When searching through the literature, different types of publications were found.
-To get an idea of the type of publications found within this sample, we distinguished between a journal article, preprint, PhD thesis, poster, draft/report, and conference paper.
-An overview is given in table xxx.
+If a document similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine if the publication matched the registration.
+Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as “not publicly shared” in any of the document types outlined above.
 
@@
 
-Because of large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
+Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
 `r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration.
@@
 These results are summarized in Table \@ref(tab:table-quality).
-The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of details in the registrations (and thus that of the research studies) does not differ much between the two groups.
+The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups.
+Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.
 
@@
 
-In the main text we have classified the reasons provided by researchers not to publish in five categories. Below, we provide a more fine-grained classification consisting of 15 categories.
+In the main text we have classified the reasons that researchers provided to not to publish their registered study in five categories.
+Below in Table \@ref(tab:reasons-non-publish) we provide a more fine-grained classification consisting of 15 categories.
 
-```{r reasons_non_publish}
+```{r reasons-non-publish}
 # Reason not published ----------------------------------------------------
@@
 While most researchers (79%) mentioned a motivation to practice open science as the primary reason for opening an OSF project (see Table \@ref(tab:reasonopen)), more diverse reasons were given for keeping the OSF project closed (see Table \@ref(tab:reasonclosed)).
-Many researchers (36%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was open.
-The second most common reason not to open the project (26%) was that researchers simply forgot to open the project.
+Many researchers (36%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was opened.
+The second most common reason not to open the project (26%) was that researchers simply forgot.
 Others made the moment to open the project dependent on the publication of the study (14%), and technical issues (e.g., a lack of familiarity or misunderstanding about the OSF) were reasons to both open a project and to keep it private (in 8% and 10% of the cases, respectively).
@@
 This is an indication of the use of the OSF by early adopters in the years up to 2017.
-One researcher appeared three times, and 3 other researchers appeared 2 times.
-Although each registration can be published or not, there is the possibility of some dependencies in the dataset because the probability that these authors publish a paper might be correlated across registrations.
-
-# References
-
-<!-- # interlinepenalty prevents freak error when a hyperlink in reference breaks across a page -->
-\begingroup
-\interlinepenalty = 10000
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
+After excluding multiple registrations for the same research project, one researcher appeared three times, and three other researchers appeared two times.
+Although each registration can be published or not, there is the possibility of some dependencies in the data set because the probability that these authors publish a paper might be correlated across registrations.

### 2023-05-29 supplement.tex
updates supplement

@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \ifLuaTeX
@@
 {}{\PatchFailed}
-\keywords{Publication Bias; File-Drawer; Registry; Research Waste\newline\indent Word count: 1111}
 \usepackage{dblfloatfix}
@@
   pdflang={en-EN},
-  pdfkeywords={Publication Bias; File-Drawer; Registry; Research Waste},
   hidelinks,
@@
 
-\caption{\label{tab:publicationtype}Type of object that matched the registration for all registrations that were publicly shared}
+\caption{\label{tab:publicationtype}Type of document that matched the registration for all registrations that were publicly shared}
 
@@
 For each user associated with a registration we retrieved a list of their publications and scanned through their publications after the registration date.
-If a paper similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine of the publication matched the registration.
-Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as ``not publicly shared''.
-
-Our use of the term `published' differs from another inception cohort study in psychology (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}) who limited `publication' to journal articles and book chapters.
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.
-
-When searching through the literature, different types of publications were found.
-To get an idea of the type of publications found within this sample, we distinguished between a journal article, preprint, PhD thesis, poster, draft/report, and conference paper.
-An overview is given in table xxx.
+If a document similar to the topic of the registration or in collaboration with some of the other OSF users associated with the registration was found, we again aimed to determine if the publication matched the registration.
+Whenever we failed to find a publication that seemed to be related to a registration the registration was marked as ``not publicly shared'' in any of the document types outlined above.
 
@@
 
-Because of large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
+Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
 18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration.
@@
 These results are summarized in Table \ref{tab:table-quality}.
-The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of details in the registrations (and thus that of the research studies) does not differ much between the two groups.
+The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups.
+Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.
 
@@
 
-In the main text we have classified the reasons provided by researchers not to publish in five categories. Below, we provide a more fine-grained classification consisting of 15 categories.
+In the main text we have classified the reasons that researchers provided to not to publish their registered study in five categories.
+Below in Table \ref{tab:reasons-non-publish} we provide a more fine-grained classification consisting of 15 categories.
 
@@
 
-\caption{\label{tab:reasons_non_publish}Summary of main reasons researchers self-reported to not publish registered studies.}
+\caption{\label{tab:reasons-non-publish}Summary of main reasons researchers self-reported to not publish registered studies.}
 
@@
 While most researchers (79\%) mentioned a motivation to practice open science as the primary reason for opening an OSF project (see Table \ref{tab:reasonopen}), more diverse reasons were given for keeping the OSF project closed (see Table \ref{tab:reasonclosed}).
-Many researchers (36\%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was open.
-The second most common reason not to open the project (26\%) was that researchers simply forgot to open the project.
+Many researchers (36\%) mentioned that the associated project does not contain any new or relevant information, so peers would not benefit if the project was opened.
+The second most common reason not to open the project (26\%) was that researchers simply forgot.
 Others made the moment to open the project dependent on the publication of the study (14\%), and technical issues (e.g., a lack of familiarity or misunderstanding about the OSF) were reasons to both open a project and to keep it private (in 8\% and 10\% of the cases, respectively).
@@
 This is an indication of the use of the OSF by early adopters in the years up to 2017.
-One researcher appeared three times, and 3 other researchers appeared 2 times.
-Although each registration can be published or not, there is the possibility of some dependencies in the dataset because the probability that these authors publish a paper might be correlated across registrations.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-
-\interlinepenalty = 10000
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-franco_publication_2014}{}}%
-Franco, A., Malhotra, N., \& Simonovits, G.
-(2014).
-Publication bias in the social sciences: {Unlocking} the file drawer.
-\emph{Science}, \emph{345}(6203), 1502--1505.
-\url{https://doi.org/10.1126/SCIENCE.1255484}
-
-\end{CSLReferences}
-
-\endgroup
+After excluding multiple registrations for the same research project, one researcher appeared three times, and three other researchers appeared two times.
+Although each registration can be published or not, there is the possibility of some dependencies in the data set because the probability that these authors publish a paper might be correlated across registrations.
 

### 2023-05-29 paper.Rmd
typo and running head

@@
 title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
-shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
+shorttitle        : "QUANTIFYING THE FILEDRAWER FOR REGISTERED STUDIES"
 author: 
@@
 Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published.
-We estimate that 5550 out of 9544 (58%) of registrations on the OSF are published within at least 4 years.
+We estimate that 5550 out of 9544 (58%) registrations on the OSF are published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.

### 2023-05-31 paper.Rmd
added extrapolation section, correcting errors.

@@
 ```{r inclusion, include = FALSE}
-
-# I need to fix the issue of number of included before and after emails.
-# We included more first, and emailed people, and then removed some data.
 
@@
 For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found.
-Of the `r match_per_classification[4,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
+Of the `r match_per_classification[4,2]` (`r round(100*match_per_classification[4,2]/sum(match_per_classification[4,2:3]),2)`%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
 In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published.
@@
 
-#Of the 14 published, 6 were from automatically opened registrations, out of 29 total closed projects, so 6/29 automatically opened projects we thought were unpublished were published.
-For the manually opened projects, 8/16 were published.
+# We did not get a response for 6 projects we were uncertain about, of which 1 was manually opened, and 5 were automatically opened.
+For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not.
+For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 19 were published.
+We did not get responses for 6 projects, of which 5 were automatically opened, and 1 was manually opened, for which the following might hold:
+
 published_after_email_per_classification$published[11]
@@
 
-# So how many of the uncertain registrations are actually published?
+# So how many of the uncertain registrations we received no response for might actually published?
+# 2.368421 out of 6, and 3.031579 are unpublished.
+
 published_non_response_uncertain <- (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10])
@@
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
-Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r unpublished_non_response_unpublished` out of `r total_assumed_unpublished_no_responses` of the registration in the unpublished classification and `r unpublished_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` of the registration in the uncertain classification are actually published.
+Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.
 
@@
                  Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
-                 Percentage_Included = c(round(included_before$mean,2), ""),
+                 Percentage_Included = c(round(100*included_before$mean,2), ""),
                  Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
-                 Published = c(round(result_manual$mean,2), round(result_auto$mean,2), ""), 
+                 Published = c(round(100*result_manual$mean,2), round(100*result_auto$mean,2), ""), 
                  Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
@@
 Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017.
-Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
+Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
 Our study provides an important datapoint to understand how many studies are performed, but never shared.
@@
 What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer.
-Researchers might feel uneasy to honestly discuss this topic because unpublished studies are strongly associated with bias.
-More transparency about unpublished studies would allow our field to improve the way we work and increase the efficiency of psychological science.
+Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication.
+More transparency about unpublished studies would allow our field to learn where we can improve how we work, thereby increasing the efficiency of psychological science.
 

### 2023-05-31 paper.tex
typo and running head
added extrapolation section, correcting errors.

@@
 
-\shorttitle{QUANTIFYING PUBLISHED REGISTERED STUDIES}
+\shorttitle{QUANTIFYING THE FILEDRAWER FOR REGISTERED STUDIES}
 
@@
 Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published.
-We estimate that 5550 out of 9544 (58\%) of registrations on the OSF are published within at least 4 years.
+We estimate that 5550 out of 9544 (58\%) registrations on the OSF are published within at least 4 years.
 Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
@@
 For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found.
-Of the 14 (28\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
+Of the 14 (56\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published.
 In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published.
@@
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
-Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 19.45 out of 26 of the registration in the unpublished classification and 3.03 out of 6 of the registration in the uncertain classification are actually published.
+Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published.
 
@@
 \midrule
-Manually Opened & 8008 & 0.55 & 4,395 & 0.86 & 3,775 & 619\\
-Automatically Opened & 9042 & 0.57 & 5,150 & 0.34 & 1,775 & 3,375\\
+Manually Opened & 8008 & 54.88 & 4,395 & 85.91 & 3,775 & 619\\
+Automatically Opened & 9042 & 56.95 & 5,150 & 34.47 & 1,775 & 3,375\\
 Total & 17050 &  & 9,544 &  & 5,550 & 3,994\\
@@
 Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017.
-Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
+Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
 Our study provides an important datapoint to understand how many studies are performed, but never shared.

### 2023-05-31 supplement.Rmd
added extrapolation section, correcting errors.

@@
 
+# Details on Extrapolating to the Population
+
+```{r published, include = FALSE}
+
+# How many are published after email when we thought before emailing they were published (1), unpublished (2), and when we were uncertain (3)?
+Divide this per classification (manually opened and automatically opened) and whether we got an email response.
+published_after_email_per_classification <- registration_data_included %>% group_by(published_before_email, email_response, classification) %>% summarise(published = sum(published_after_email == 1), not_published = sum(published_after_email == 2), unsure = sum(published_after_email == 3))
+published_after_email_per_classification
+
+# How many did we think unpublished before emails?
+total_assumed_unpublished <- sum(published_after_email_per_classification$published[5:8], published_after_email_per_classification$not_published[5:8])
+
+# Of those, how many did we get a reply for?
+total_assumed_unpublished_responses <- sum(published_after_email_per_classification$published[7:8], published_after_email_per_classification$not_published[7:8])
+
+# Of those, how many did we not get a reply for?
+total_assumed_unpublished_no_responses <- sum(published_after_email_per_classification$published[5:6], published_after_email_per_classification$not_published[5:6])
+
+# For the 45 we got responses about, 14 were actually published, and 31 were not.
+sum(published_after_email_per_classification$published[7:8])
+sum(published_after_email_per_classification$not_published[7:8])
+
+# Of the 14 published, 6 were from automatically opened registrations, out of 29 total closed projects, so 6/29 automatically opened projects we thought were unpublished were published.
+For the manually opened projects, 8/16 were published.
+published_after_email_per_classification$published[7]
+published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]
+published_after_email_per_classification$published[8]
+published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]
+
+# We did not get responses for 26 projects, of which 22 were automatically opened, and 4 were manually opened, for which the following might hold: 
+# 8/16 of the 4 manually opened registrations could be published.
+# 6/29 of the 22 automatically opened registrations could be published
+total_assumed_unpublished_no_responses
+published_after_email_per_classification$not_published[5]
+published_after_email_per_classification$not_published[6]
+
+published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]
+
+published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]
+
+# So how many of the assumed unpublished are actually published?
+published_non_response_unpublished <- ((published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]) + (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]))
+
+unpublished_non_response_unpublished <- total_assumed_unpublished_no_responses - ((published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]) + (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]))
+
+# Now for uncertain projects
+
+# How many were we uncertain about before emails? 30
+total_assumed_unpublished_uncertain <- sum(published_after_email_per_classification$published[9:12], published_after_email_per_classification$not_published[9:12], published_after_email_per_classification$unsure[9:12])
+
+# Of those, how many did we get a reply for?
+total_assumed_unpublished_uncertain_responses <-  sum(published_after_email_per_classification$published[11:12], published_after_email_per_classification$not_published[11:12], published_after_email_per_classification$unsure[11:12])
+
+# Of those, how many did we not get a reply for?
+total_assumed_unpublished_uncertain_no_responses <-  sum(published_after_email_per_classification$published[9:10], published_after_email_per_classification$not_published[9:10], published_after_email_per_classification$unsure[9:10])
+
+# For the 24 we got responses about, 12 were actually published, and 12 were not.
+sum(published_after_email_per_classification$published[11:12])
+sum(published_after_email_per_classification$not_published[11:12])
+
+# We did not get a response for 6 projects we were uncertain about, of which 1 was manually opened, and 5 were automatically opened.
+For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not.
+For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 19 were published.
+We did not get responses for 6 projects, of which 5 were automatically opened, and 1 was manually opened, for which the following might hold:
+
+published_after_email_per_classification$published[11]
+published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]
+published_after_email_per_classification$published[12]
+published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]
+
+# We did not get a response for 6 projects we were uncertain about, of which 1 was manually opened, and 5 were automatically opened.
+For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not.
+For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 10 were published.
+We did not get responses for 6 projects, of which 5 were automatically opened, and 1 was manually opened, for which the following might hold:
+
+total_assumed_unpublished_uncertain_no_responses
+published_after_email_per_classification$unsure[9]
+published_after_email_per_classification$unsure[10]
+
+published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]
+
+published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]
+
+# So how many of the uncertain registrations we received no response for might actually published?
+# 2.368421 out of 6, and 3.031579 are unpublished.
+
+published_non_response_uncertain <- (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10])
+
+unpublished_non_response_uncertain <- total_assumed_unpublished_uncertain_no_responses - ((published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]))
+
+# For manually opened registrations, altogether the % of published studies is:
+
+published_manual <- published_after_email_per_classification$published[2] + published_after_email_per_classification$published[4] + published_after_email_per_classification$published[7] + published_after_email_per_classification$published[11] + published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5] + published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]
+
+# For automatically opened registrations (classification 2), altogether the % of published studies is: 
+# 6 we classified as published, 6 published we thought unpublished but confirmed in email response, +9 confirmed unpublished we were uncertain about, + 5 * 9/19 for the 5 unsure without response, and those we thought unpublished predicted to be published.
+published_auto <- published_after_email_per_classification$published[3] + published_after_email_per_classification$published[8] + published_after_email_per_classification$published[12] + published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10] + published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]
+
+# And the unpublished studies for manually opened registrations is:
+unpublished_manual <- published_after_email_per_classification$not_published[7] + published_after_email_per_classification$not_published[11] + (1 - (published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]))) * published_after_email_per_classification$not_published[5] + (1 - (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]))) * published_after_email_per_classification$unsure[9]
+
+# And the unpublished automatically opened studies are:
+unpublished_auto <- published_after_email_per_classification$not_published[8] + published_after_email_per_classification$not_published[12] + (1 - (published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]))) * published_after_email_per_classification$not_published[6] + (1 - (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]))) * published_after_email_per_classification$unsure[10]
+
+# Check to see if they combine to 169 total included:
+published_manual + published_auto + unpublished_manual + unpublished_auto
+
+# Compute CI around estimates per group
+result_total <- binom.confint(x = published_manual + published_auto, n = published_manual + unpublished_manual + published_auto + unpublished_auto, tol = 1e-8, method = "wilson")
+result_manual <- binom.confint(x = published_manual, n = published_manual + unpublished_manual, tol = 1e-8, method = "wilson")
+result_auto <- binom.confint(x = published_auto, n = published_auto + unpublished_auto, tol = 1e-8, method = "wilson")
+
+```
+
+Before emailing authors, we believed `r total_assumed_unpublished` articles remained unpublished.
+We received responses for `r total_assumed_unpublished_responses` registrations after emailing researchers, and we did not get a response for `r total_assumed_unpublished_no_responses` registrations.
+Based on these responses we learned that out that of all registrations we thought were unpublished `r sum(published_after_email_per_classification$published[7:8])` were actually published, and `r sum(published_after_email_per_classification$not_published[7:8])` remained unpublished.
+We will compute the probability that a paper is published, even though we believed it was unpublished both for registrations classified as automatically opened (`r published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]` out of `r total_assumed_unpublished_responses`), and manually opened (`r published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]` out of `r total_assumed_unpublished_responses`).
+
+Of the `r published_after_email_per_classification$published[7] + published_after_email_per_classification$published[8]` registrations researchers informed us were actually published, `r published_after_email_per_classification$published[8]` were from registrations classified as automatically opened (out of `r published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]` automatically opened registrations that we received a response for), so `r published_after_email_per_classification$published[8]`/`r published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]` registrations classified as automatically opened that we thought were unpublished were actually published.
+For the registrations classified as manually opened, `r published_after_email_per_classification$published[7]` out of `r published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]` were published.
+
+We can use these two percentages to extrapolate to the `r total_assumed_unpublished_no_responses` registrations we did not get a response to our email for.
+Of these `r total_assumed_unpublished_no_responses`, `r published_after_email_per_classification$not_published[6]` were classified as automatically opened, and `r published_after_email_per_classification$not_published[5]` were classified as manually opened, for which the following might hold.
+8/16 of the `r published_after_email_per_classification$not_published[5]` manually opened registrations could be published (which equals `r published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]` published registrations), and `r published_after_email_per_classification$published[8]`/`r published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]` of the `r published_after_email_per_classification$not_published[6]` automatically opened registrations could be published (which equals `r published_after_email_per_classification$published[8]/ (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8])` * `r published_after_email_per_classification$not_published[6]` = `r
+published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]` registrations).
+So an additional `r published_non_response_unpublished` registrations should be considered published, and `r unpublished_non_response_unpublished` remain unpublished.
+
+We can repeat these extrapolations for the registrations we were uncertain about.
+We were uncertain about `r total_assumed_unpublished_uncertain` registrations (often due to a lack of information in the registration).
+Of those we got a reply for `r total_assumed_unpublished_uncertain_responses`.
+For the `r total_assumed_unpublished_uncertain_responses` registrations we were uncertain about that we did received a response for, `r sum(published_after_email_per_classification$published[11:12])` are published, and `r sum(published_after_email_per_classification$not_published[11:12])` are not.
+For the manually opened projects, `r published_after_email_per_classification$published[11]` out of `r published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]` were published, and for the automatically opened projects `r published_after_email_per_classification$published[12]` out of `r published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]` were published.
+Of the `r sum(published_after_email_per_classification$unsure[9:10])` registrations we did not received a reply for, `r published_after_email_per_classification$unsure[9:10][1]` was manually opened, and `r published_after_email_per_classification$unsure[9:10][2]` were automatically opened.
+So on average `r published_after_email_per_classification$published[11]`/`r (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11])` * `r published_after_email_per_classification$unsure[9]` = `r published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]` registrations classified as manually opened will be published, and `r published_after_email_per_classification$published[12]`/`r (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12])` * `r published_after_email_per_classification$unsure[10]` = `r published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]` registrations classified as automatically opened will be published, for a total of `r published_non_response_uncertain`.
+
+Altogether, for automatically opened registrations the percentage of published studies is `r published_after_email_per_classification$published[3]` we classified as published, `r published_after_email_per_classification$published[8]` registrations we thought were unpublished, but through email responses learned were published, `r published_after_email_per_classification$published[12]` we were originally uncertain about but were confirmed unpublished in an email response, `r published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10]` for the 5 we initially were unsure about but were predicted to be published had researchers replied to our emails, and the `r published_after_email_per_classification$published[8] / (published_after_email_per_classification$published[8] + published_after_email_per_classification$not_published[8]) * published_after_email_per_classification$not_published[6]` we initially thought were unpublished but were predicted to be published had researchers replied to our emails, for a total of `r published_auto` published automatically opened articles out of a total of `r (published_auto + unpublished_auto)` (`r 100*published_auto/(published_auto + unpublished_auto)`%).
+
+For automatically opened registrations the percentage of published studies is `r published_after_email_per_classification$published[2] + published_after_email_per_classification$published[4]` we classified as published, `r published_after_email_per_classification$published[7]` registrations we thought were unpublished, but through email responses learned were published, `r published_after_email_per_classification$published[11]` we were originally uncertain about but were confirmed unpublished in an email response, `r published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]` we initially were unsure about but were predicted to be published had researchers replied to our emails, and the `r published_after_email_per_classification$published[7] / (published_after_email_per_classification$published[7] + published_after_email_per_classification$not_published[7]) * published_after_email_per_classification$not_published[5]` we initially thought were unpublished but were predicted to be published had researchers replied to our emails, for a total of `r published_manual` published manually opened articles out of a total of `r (published_manual + unpublished_manual)` (`r 100*published_manual/(published_manual + unpublished_manual)`%).
+
+These two estimated percentages of the number of published studies in the registrations classified as manually opened and automatically opened are used in Table 3 in the main document to extrapolate from our sample to the number of published articles in the entire population of registrations we retrieved from the OSF up to November 2017.
+
 # Extensiveness of the details in registrations

### 2023-05-31 supplement.tex
added extrapolation section, correcting errors.

@@
 
+\hypertarget{details-on-extrapolating-to-the-population}{%
+\section{Details on Extrapolating to the Population}\label{details-on-extrapolating-to-the-population}}
+
+Before emailing authors, we believed 71 articles remained unpublished.
+We received responses for 45 registrations after emailing researchers, and we did not get a response for 26 registrations.
+Based on these responses we learned that out that of all registrations we thought were unpublished 14 were actually published, and 31 remained unpublished.
+We will compute the probability that a paper is published, even though we believed it was unpublished both for registrations classified as automatically opened (29 out of 45), and manually opened (16 out of 45).
+
+Of the 14 registrations researchers informed us were actually published, 6 were from registrations classified as automatically opened (out of 29 automatically opened registrations that we received a response for), so 6/29 registrations classified as automatically opened that we thought were unpublished were actually published.
+For the registrations classified as manually opened, 8 out of 16 were published.
+
+We can use these two percentages to extrapolate to the 26 registrations we did not get a response to our email for.
+Of these 26, 22 were classified as automatically opened, and 4 were classified as manually opened, for which the following might hold.
+8/16 of the 4 manually opened registrations could be published (which equals 2 published registrations), and 6/29 of the 22 automatically opened registrations could be published (which equals 0.21 * 22 = 4.55 registrations).
+So an additional 6.55 registrations should be considered published, and 19.45 remain unpublished.
+
+We can repeat these extrapolations for the registrations we were uncertain about.
+We were uncertain about 30 registrations (often due to a lack of information in the registration).
+Of those we got a reply for 24.
+For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not.
+For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 19 were published.
+Of the6 registrations we did not received a reply for, 1 was manually opened, and 5 were automatically opened.
+So on average 3/5 * 1 = 0.60 registrations classified as manually opened will be published, and 9/19 * 5 = 2.37 registrations classified as automatically opened will be published, for a total of 2.97.
+
+Altogether, for automatically opened registrations the percentage of published studies is 6 we classified as published, 6 registrations we thought were unpublished, but through email responses learned were published, 9 we were originally uncertain about but were confirmed unpublished in an email response, 2.37 for the 5 we initially were unsure about but were predicted to be published had researchers replied to our emails, and the 4.55 we initially thought were unpublished but were predicted to be published had researchers replied to our emails, for a total of 27.92 published automatically opened articles out of a total of 81 (34.47\%).
+
+For automatically opened registrations the percentage of published studies is 62 we classified as published, 8 registrations we thought were unpublished, but through email responses learned were published, 3 we were originally uncertain about but were confirmed unpublished in an email response, 0.60 we initially were unsure about but were predicted to be published had researchers replied to our emails, and the 2 we initially thought were unpublished but were predicted to be published had researchers replied to our emails, for a total of 75.60 published manually opened articles out of a total of 88 (85.91\%).
+
+These two estimated percentages of the number of published studies in the registrations classified as manually opened and automatically opened are used in Table 3 in the main document to extrapolate from our sample to the number of published articles in the entire population of registrations we retrieved from the OSF up to November 2017.
+
 \hypertarget{extensiveness-of-the-details-in-registrations}{%

### 2023-06-01 paper.Rmd
final updates based on feedback

@@
 author: 
-  - name          : "Eline Ensinck"
+  - name          : "Eline N. F. Ensinck"
     affiliation   : "1"
@@
   This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
-The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
-We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft.
+A computationally reproducible manuscript is available at https://github.com/Lakens/registered_published and data and materials on https://osf.io/8uqfb/.
+We are grateful to Stephen Lindsay, Cristian Mesquida Caldentey, Henry Wyneken, and Gerda Wyssen for feedback on a draft.
 abstract: |
-  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared.
+  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared within at least 4 years.
 Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published.
@@
 For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992].
-In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
+In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 45% were published in a scientific journal or as a book chapter, 29% were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
 
@@
 
-Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
+Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of performed studies that become known to peers, compared to registries where registrations can remain closed indefinitely.
 By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions.
@@
 And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?
-Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
+Answers to these questions can provide insights into the benefits of a platform that makes registrations public after an embargo period (e.g., OSF), compared to platforms where users can choose to make their registration public or not (e.g., AsPredicted.org).
 
-Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not.
+Our third question concerns the possibility for fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not.
 For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished.
@@
 Registrations are part of at least one associated project page on the OSF.
-Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample.
+Sometimes researchers still work on projects four years after a registration, and we saw continued activity in a few registrations in our sample.
 The final classification was based on whether the projects were public in April 2022.
@@
 
-*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ).
+*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years).
+We had no justification for our sample size given uncertainty about the number of studies that would fit our inclusion criteria but relied on an informal trade-off between time constraints and sufficiently accurate estimates.
 The OSF API does not provide information about how a project has been made public.
@@
 *Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021].
-We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results.
+We considered a study ‘published’ if the study was communicated in a way that allows other researchers to learn about the results.
 In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail).
@@
 If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration.
-In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration.
+In many cases, especially when registrations on the OSF contained little information (see the supplement for details on how much information registrations contained), and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration.
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
@@
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
-Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.
+Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.
 
@@
 After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]).
-Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations.
+Our sample contained an almost equal number of manually opened and automatically opened registrations to examine our research question about the consequences of automatically opening registrations after an embargo.
 As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
@@
 This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community.
-We estimate that `r round(100*result_auto[4], 2)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 2)`] of automatically opened registrations is published.
-Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
+We estimate that `r round(100*result_auto[4], 1)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 1)`] of automatically opened registrations is published.
+Consequently, `r 100-round(100*result_auto[4], )`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
 In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
@@
 Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities.
-In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.
+Only twice did researchers respond that the project was still in progress, which suggests most projects will not appear in the future, but we did see ongoing research activity in a small number of projects.
 
@@
 
-Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017.
+Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 1)`%, for all registrations on the Open Science framework that were created before November 18, 2017.
 Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
@@
 The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
-Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.
+Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009].
 
@@
 The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017].
-It is possible that the  absence of these studies contributes to publication bias in the scientific literature.
+It is probable that the  absence of these studies contributes to publication bias in the scientific literature.
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014].
@@
 At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
-In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
+It should be noted that In fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
 Our study demonstrates that the percentage of unpublished studies can be high.
@@
 This means that, for example, in the “OSF-Standard Pre-Data Collection Registration” the only information that becomes visible is the answer to the question “Has data collection begun for this project?”, the answer to the question “Have you looked at the data?”, and the text in the field “Other comments”.
-Some users wrote in this field “See the preregistration document specifying the logic, hypotheses, and analyses” but that files is not made accessible.
+Some users wrote in this field “See the preregistration document specifying the logic, hypotheses, and analyses” but those files are not made accessible when the registration is made public after four years.
 If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the “Other comments” field.
@@
 Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication.
-More transparency about unpublished studies would allow our field to learn where we can improve how we work, thereby increasing the efficiency of psychological science.
+More transparency about unpublished studies would allow academics to learn where they can improve the way they work, thereby increasing the efficiency of scientific research.
 

### 2023-06-01 supplement.Rmd
final updates based on feedback

@@
 
-# Extensiveness of the details in registrations
+# Extensiveness of Information in Registrations
 
@@
 
-# Fine-grained categorization of reasons for non-publication
+# Fine-Grained Categorization of Reasons for Non-Publication
 
-In the main text we have classified the reasons that researchers provided to not to publish their registered study in five categories.
+In the main text we have classified the reasons that researchers provided to not publish their registered study in five categories.
 Below in Table \@ref(tab:reasons-non-publish) we provide a more fine-grained classification consisting of 15 categories.
@@
 
-# It matters if this is done on all registrations we emailed for, or just the ones we ended up including.
-
-reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(a = sum(reason_if_unpublished == 1), b = sum(reason_if_unpublished == 2), c = sum(reason_if_unpublished == 3), d = sum(reason_if_unpublished == 4), e = sum(reason_if_unpublished == 5), f = sum(reason_if_unpublished == 6), h = sum(reason_if_unpublished == 7), i = sum(reason_if_unpublished == 8), j = sum(reason_if_unpublished == 9), k = sum(reason_if_unpublished == 10), l = sum(reason_if_unpublished == 11), m = sum(reason_if_unpublished == 12), n = sum(reason_if_unpublished == 13), o = sum(reason_if_unpublished == 14), p = sum(reason_if_unpublished == 15), q = sum(reason_if_unpublished == 16))
+reasons_table <- registration_data %>% group_by(classification) %>% summarise(a = sum(reason_if_unpublished == 1), b = sum(reason_if_unpublished == 2), c = sum(reason_if_unpublished == 3), d = sum(reason_if_unpublished == 4), e = sum(reason_if_unpublished == 5), f = sum(reason_if_unpublished == 6), h = sum(reason_if_unpublished == 7), i = sum(reason_if_unpublished == 8), j = sum(reason_if_unpublished == 9), k = sum(reason_if_unpublished == 10), l = sum(reason_if_unpublished == 11), m = sum(reason_if_unpublished == 12), n = sum(reason_if_unpublished == 13), o = sum(reason_if_unpublished == 14), p = sum(reason_if_unpublished == 15), q = sum(reason_if_unpublished == 16))
 reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
@@
 
-\newpage
-
 # Motivations for opening or not opening OSF project pages

### 2023-06-01 supplement.tex
final updates based on feedback

@@
   pdftitle={Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
-  pdfauthor={Eline Ensinck1 \& Daniël Lakens1},
+  pdfauthor={Eline N. F. Ensinck1 \& Daniël Lakens1},
   pdflang={en-EN},
@@
 \title{Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
-\author{Eline Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
+\author{Eline N. F. Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
 \date{}
@@
 For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 19 were published.
-Of the6 registrations we did not received a reply for, 1 was manually opened, and 5 were automatically opened.
+Of the 6 registrations we did not received a reply for, 1 was manually opened, and 5 were automatically opened.
 So on average 3/5 * 1 = 0.60 registrations classified as manually opened will be published, and 9/19 * 5 = 2.37 registrations classified as automatically opened will be published, for a total of 2.97.
@@
 
-\hypertarget{extensiveness-of-the-details-in-registrations}{%
-\section{Extensiveness of the details in registrations}\label{extensiveness-of-the-details-in-registrations}}
+\hypertarget{extensiveness-of-information-in-registrations}{%
+\section{Extensiveness of Information in Registrations}\label{extensiveness-of-information-in-registrations}}
 
@@
 \hypertarget{fine-grained-categorization-of-reasons-for-non-publication}{%
-\section{Fine-grained categorization of reasons for non-publication}\label{fine-grained-categorization-of-reasons-for-non-publication}}
+\section{Fine-Grained Categorization of Reasons for Non-Publication}\label{fine-grained-categorization-of-reasons-for-non-publication}}
 
-In the main text we have classified the reasons that researchers provided to not to publish their registered study in five categories.
+In the main text we have classified the reasons that researchers provided to not publish their registered study in five categories.
 Below in Table \ref{tab:reasons-non-publish} we provide a more fine-grained classification consisting of 15 categories.
@@
 Failed replication & 1 & 3 & 4\\
-Unfinished study & 1 & 5 & 6\\
-Educational project & 0 & 0 & 0\\
+Unfinished study & 1 & 6 & 7\\
+Educational project & 1 & 3 & 4\\
 Pilot & 0 & 1 & 1\\
@@
 Shared with funder (not the goal to publish) & 0 & 1 & 1\\
-Lack of time / busy with other projects & 1 & 3 & 4\\
+Lack of time / busy with other projects & 2 & 4 & 6\\
 Conflicting / unclear results & 0 & 3 & 3\\
@@
 
-\newpage
-
 \hypertarget{motivations-for-opening-or-not-opening-osf-project-pages}{%

### 2023-06-18 paper.Rmd
minor changes

@@
 abstract: |
-  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared within at least 4 years.
-Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published.
-We estimate that 5550 out of 9544 (58%) registrations on the OSF are published within at least 4 years.
-Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
-In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
-Our study shows that a substantial amount of data that researchers collect is never publicly shared.
+  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared after at least 4 years.
+Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (61.3%) were published.
+We estimate that 5550 out of 9544 (58.2%) registered studies on the OSF are published.
+Researchers use registries to make unpublished studies public, and the OSF policy to open registrations after a four year embargo substantially increases the number of studies that become known to the scientific community.
+In responses to emails asking researchers why studies remained unpublished logistical issues (e.g., lack of time, researchers changing jobs) were the most common cause, followed by null results, and rejections during peer review.
+Our study shows that a substantial amount of studies researchers perform remain unpublished.
 
@@
 For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992].
-In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 45% were published in a scientific journal or as a book chapter, 29% were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
+In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 large studies on nationally representative samples 45% were published in a scientific journal or as a book chapter, 29% were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.
 
@@
 However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013].
-The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.
+The OSF offers researchers the possibility to voluntarily register their study and specify information about the study rationale and methods.
 
-One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ].
-This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago.
-It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
+One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) is made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ].
+Because of this policy the OSF provides a public record of all studies that were registered on the platform up to four years ago.
+It is therefore possible to use the database of registrations for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
 
@@
 
-Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of performed studies that become known to peers, compared to registries where registrations can remain closed indefinitely.
-By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions.
+Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of studies that become known to peers, compared to registries where registrations can remain closed indefinitely.
+By comparing the publication status of registrations that researchers manually made public with registrations automatically opened by the OSF we can answer two questions.
 How often do researchers voluntarily share information about their study, even when the study remains unpublished?
-And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?
+And how often do we learn about performed but unpublished studies because registrations are automatically made public after four years?
 Answers to these questions can provide insights into the benefits of a platform that makes registrations public after an embargo period (e.g., OSF), compared to platforms where users can choose to make their registration public or not (e.g., AsPredicted.org).
 
-Our third question concerns the possibility for fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not.
-For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished.
+Our third question examined whether fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not.
+For a registry to notify the scientific community about the presence of unpublished studies the information in the registry needs to be extensive enough to match the registration to a published study, or to conclude the registered study remains unpublished.
 As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
@@
 
-*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021].
-We considered a study ‘published’ if the study was communicated in a way that allows other researchers to learn about the results.
+*Classifying Publication Status*: Studies can be made available in different ways [@lishner_sorting_2021].
+We considered a study published if the study was communicated in a way that allows other researchers to learn about the results.
 In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail).
@@
 Our definition of ‘published’ is broader than in previous inception cohort studies (e.g., @dickersin_factors_1992; @franco_publication_2014).
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
+We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
 
@@
 In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not.
-If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration.
+If a publication could be found that provided a direct link to the OSF we could be certain that we found the publication corresponding to the registration.
 In many cases, especially when registrations on the OSF contained little information (see the supplement for details on how much information registrations contained), and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration.
@@
 
-For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers.
+For all registrations where we were uncertain about whether a publication corresponded to the registration we attempted to retrieve contact information of researchers involved, and contacted the researchers.
 We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished.
-We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` researchers with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*replies_per_group$sum[1]/contacted_researchers_per_group$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*replies_per_group$sum[2]/contacted_researchers_per_group$sum[2],2)`%) replied to our email with additional information to update our classification.
-We sent `r numbers_to_words(contacted_researchers_per_publication_status$sum[2])` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r numbers_to_words(responses_per_publication_status$sum[2])` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses).
+We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` researchers with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*replies_per_group$sum[1]/contacted_researchers_per_group$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*replies_per_group$sum[2]/contacted_researchers_per_group$sum[2],2)`%) replied to our questions with additional information to update our classification.
+We sent `r numbers_to_words(contacted_researchers_per_publication_status$sum[2])` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r numbers_to_words(responses_per_publication_status$sum[2])` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses).
 Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
@@
 
-After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%.
+After updating our classification based on responses the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%.
 Sometimes a publication we found in the literature did not belong to the registration.
 If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
-In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found.
+In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses matched with publications we found.
 For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.
@@
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
-Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.
+Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published (see supplement for details).
 
@@
 
-After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]).
+After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response (see the supplement for details), we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r round(result_total$x, 1)` registered studies are published (`r round(100*result_total[4], 1)`%, 95% CI [`r round(100*result_total[5], 1)`; `r round(100*result_total[6], 1)`]).
 Our sample contained an almost equal number of manually opened and automatically opened registrations to examine our research question about the consequences of automatically opening registrations after an embargo.
@@
 Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished.
-Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
+Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 1)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
 
@@
 
-We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
-In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
+We see that `r round(100*result_manual[4], 1)`%, 95% CI [`r round(100*result_manual[5], 1)`; `r round(100*result_manual[6], 1)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
+In the remaining `r 100-round(100*result_manual[4], 1)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
 This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community.
-We estimate that `r round(100*result_auto[4], 1)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 1)`] of automatically opened registrations is published.
-Consequently, `r 100-round(100*result_auto[4], )`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
+We estimate that `r round(100*result_auto[4], 1)`%, 95% CI [`r round(100*result_auto[5], 1)`; `r round(100*result_auto[6], 1)`] of automatically opened registrations are published.
+Consequently, `r 100-round(100*result_auto[4], 1)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
 In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
@@
 
-According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample.
+According to the self-reported causes for non-publication researchers shared with us logistical issues are the biggest cause of unpublished studies in our sample.
 Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities.
@@
 When asked why researchers made their OSF project page open, most researchers (`r reasons_open_project_table[1]` out of `r sum(reasons_open_project_table)`) mentioned a motivation to practice open science.
-Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), were waiting until a project was published (`r reasons_closed_project_table[2]` times), or experienced technical issues (`r reasons_closed_project_table[5]` times).
+Out of `r sum(reasons_closed_project_table)` responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (`r reasons_closed_project_table[3]` times), researchers forgot to open it (`r reasons_closed_project_table[6]` times), researchers were waiting until a project was published (`r reasons_closed_project_table[2]` times), or they experienced technical issues (`r reasons_closed_project_table[5]` times).
 For more details, see the online supplement.
-Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
-Although not all of the email respondents answered this question, `r sum(registration_data$four_years_known == 1)` of the researchers indicated they were aware of this policy, and `r sum(registration_data$four_years_known == 0)` were not aware of this policy.
+Finally, we were interested in how many researchers who registered on the OSF before 2017 were aware of the OSF policy to automatically open all registrations after four years.
+Although not all researchers answered this question, `r sum(registration_data$four_years_known == 1)` of the researchers indicated they were aware of this policy, and `r sum(registration_data$four_years_known == 0)` were not aware of this policy.
 
@@
 
-Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 1)`%, for all registrations on the Open Science framework that were created before November 18, 2017.
-Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
-Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
+Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 1)`% for all registrations on the Open Science framework that were created before November 18, 2017.
+Extrapolating from our sample to the population of all registrations up to November 2017, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished.
+Our study provides an important data point to understand how many studies are performed, but remain unpublished.
+The possibility that around `r 100-round(100*result_population[4], 1)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
 Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009].
@@
 Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF.
-Our estimate might not generalize to non-registered studies.
+Our estimate might not generalize to non-registered studies, nor to educational research projects.
 The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic).
@@
 At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
-It should be noted that In fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
+It should be noted that in fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), where researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and where all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
 Our study demonstrates that the percentage of unpublished studies can be high.
-The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
-Empirically examining the size of the file drawer can determine if there is room for improvement.
+Empirically examining the size of the file drawer can determine where there is room for improvement.
 
@@
 We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed.
-To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘preregistration’ from ‘data archiving’).
-Allowing users to distinguish educational projects from research projects might also be useful.
+To be able to distinguish these uses of registries, different categories of registrations could be created (e.g., distinguishing ‘preregistration’ from ‘data archiving’, with perhaps an additional category for 'educational projects').
 It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF.

### 2023-06-18 paper.tex
minor changes

@@
   pdftitle={An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
-  pdfauthor={Eline Ensinck1 \& Daniël Lakens1},
+  pdfauthor={Eline N. F. Ensinck1 \& Daniël Lakens1},
   pdflang={en-EN},
@@
 \title{An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
-\author{Eline Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
+\author{Eline N. F. Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
 \date{}
@@
 This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
-The computationally reproducible version of this manuscript is available at \url{https://github.com/Lakens/registered_published} and additional materials on \url{https://osf.io/8uqfb/}.
-We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft.
+A computationally reproducible manuscript is available at \url{https://github.com/Lakens/registered_published} and data and materials on \url{https://osf.io/8uqfb/}.
+We are grateful to Stephen Lindsay, Cristian Mesquida Caldentey, Henry Wyneken, and Gerda Wyssen for feedback on a draft.
 
@@
 \abstract{%
-We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared.
-Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published.
-We estimate that 5550 out of 9544 (58\%) registrations on the OSF are published within at least 4 years.
-Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community.
-In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review.
-Our study shows that a substantial amount of data that researchers collect is never publicly shared.
+We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared after at least 4 years.
+Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (61.3\%) were published.
+We estimate that 5550 out of 9544 (58.2\%) registered studies on the OSF are published.
+Researchers use registries to make unpublished studies public, and the OSF policy to open registrations after a four year embargo substantially increases the number of studies that become known to the scientific community.
+In responses to emails asking researchers why studies remained unpublished logistical issues (e.g., lack of time, researchers changing jobs) were the most common cause, followed by null results, and rejections during peer review.
+Our study shows that a substantial amount of studies researchers perform remain unpublished.
 }
@@
 For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}).
-In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
+In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 large studies on nationally representative samples 45\% were published in a scientific journal or as a book chapter, 29\% were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.
 
@@
 However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain (\protect\hyperlink{ref-spies_open_2013}{Spies, 2013}).
-The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.
+The OSF offers researchers the possibility to voluntarily register their study and specify information about the study rationale and methods.
 
-One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) will be made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}.
-This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago.
-It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
+One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) is made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}.
+Because of this policy the OSF provides a public record of all studies that were registered on the platform up to four years ago.
+It is therefore possible to use the database of registrations for an inception cohort study that quantifies how many studies are performed, but never publicly shared.
 
@@
 
-Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies.
-By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions.
+Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of studies that become known to peers, compared to registries where registrations can remain closed indefinitely.
+By comparing the publication status of registrations that researchers manually made public with registrations automatically opened by the OSF we can answer two questions.
 How often do researchers voluntarily share information about their study, even when the study remains unpublished?
-And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?
-Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).
+And how often do we learn about performed but unpublished studies because registrations are automatically made public after four years?
+Answers to these questions can provide insights into the benefits of a platform that makes registrations public after an embargo period (e.g., OSF), compared to platforms where users can choose to make their registration public or not (e.g., AsPredicted.org).
 
-Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not.
-For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished.
+Our third question examined whether fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not.
+For a registry to notify the scientific community about the presence of unpublished studies the information in the registry needs to be extensive enough to match the registration to a published study, or to conclude the registered study remains unpublished.
 As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
@@
 
-\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ).
+\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years).
+We had no justification for our sample size given uncertainty about the number of studies that would fit our inclusion criteria but relied on an informal trade-off between time constraints and sufficiently accurate estimates.
 The OSF API does not provide information about how a project has been made public.
@@
 
-\emph{Classifying Publication Status}: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
-We considered a study `published' if the study was communicated in any form that allows other researchers to learn about the results.
+\emph{Classifying Publication Status}: Studies can be made available in different ways (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}).
+We considered a study published if the study was communicated in a way that allows other researchers to learn about the results.
 In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail).
@@
 (\protect\hyperlink{ref-franco_publication_2014}{2014})).
-We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
+We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.
 
@@
 In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not.
-If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration.
-In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration.
+If a publication could be found that provided a direct link to the OSF we could be certain that we found the publication corresponding to the registration.
+In many cases, especially when registrations on the OSF contained little information (see the supplement for details on how much information registrations contained), and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration.
 Furthermore, if no publication could be found, there always remained the possibility that we failed to find it.
@@
 
-For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers.
+For all registrations where we were uncertain about whether a publication corresponded to the registration we attempted to retrieve contact information of researchers involved, and contacted the researchers.
 We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished.
-We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification.
-We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses).
+We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our questions with additional information to update our classification.
+We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses).
 Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.
 
-After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%.
+After updating our classification based on responses the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%.
 Sometimes a publication we found in the literature did not belong to the registration.
 If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers.
-In total, 48 of the 76 responses match with publications we found.
+In total, 48 of the 76 responses matched with publications we found.
 For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.
@@
 Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration.
-Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published.
+Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published (see supplement for details).
 
@@
 
-After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}).
-Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations.
+After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response (see the supplement for details), we predict that out of a total of 169 included registrations, 103.50 registered studies are published (61.3\%, 95\% CI {[}53.7; 68.3{]}).
+Our sample contained an almost equal number of manually opened and automatically opened registrations to examine our research question about the consequences of automatically opening registrations after an embargo.
 As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations.
 Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that 5550 registrations are published, and 3994 remain unpublished.
-Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
+Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.2\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.
 
@@
 
-We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
-In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
+We see that 85.9\%, 95\% CI {[}77.1; 91.7{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published.
+In the remaining 14.1\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published.
 This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community.
-We estimate that 34.47\%, 95\% CI {[}25.04; 45.31{]} of automatically opened registrations is published.
-Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
+We estimate that 34.5\%, 95\% CI {[}25; 45.3{]} of automatically opened registrations are published.
+Consequently, 65.5\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years.
 In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
@@
 
-According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample.
+According to the self-reported causes for non-publication researchers shared with us logistical issues are the biggest cause of unpublished studies in our sample.
 Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities.
-In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.
+Only twice did researchers respond that the project was still in progress, which suggests most projects will not appear in the future, but we did see ongoing research activity in a small number of projects.
 
@@
 When asked why researchers made their OSF project page open, most researchers (18 out of 23) mentioned a motivation to practice open science.
-Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), were waiting until a project was published (6 times), or experienced technical issues (4 times).
+Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), researchers were waiting until a project was published (6 times), or they experienced technical issues (4 times).
 For more details, see the online supplement.
-Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years.
-Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.
+Finally, we were interested in how many researchers who registered on the OSF before 2017 were aware of the OSF policy to automatically open all registrations after four years.
+Although not all researchers answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.
 
@@
 
-Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017.
-Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
-Our study provides an important datapoint to understand how many studies are performed, but never shared.
-The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
-Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.
+Our examination of 169 registrations led to an estimated publication rate of 58.2\% for all registrations on the Open Science framework that were created before November 18, 2017.
+Extrapolating from our sample to the population of all registrations up to November 2017, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished.
+Our study provides an important data point to understand how many studies are performed, but remain unpublished.
+The possibility that around 41.8\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research.
+Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).
 
@@
 The fact that for 25\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}).
-It is possible that the absence of these studies contributes to publication bias in the scientific literature.
+It is probable that the absence of these studies contributes to publication bias in the scientific literature.
 Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}).
@@
 At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts.
-In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
+It should be noted that in fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), where researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and where all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies.
 Our study demonstrates that the percentage of unpublished studies can be high.
-The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.
-Empirically examining the size of the file drawer can determine if there is room for improvement.
+Empirically examining the size of the file drawer can determine where there is room for improvement.
 
@@
 We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed.
-To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `preregistration' from `data archiving').
-Allowing users to distinguish educational projects from research projects might also be useful.
+To be able to distinguish these uses of registries, different categories of registrations could be created (e.g., distinguishing `preregistration' from `data archiving', with perhaps an additional category for `educational projects').
 It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF.
@@
 This means that, for example, in the ``OSF-Standard Pre-Data Collection Registration'' the only information that becomes visible is the answer to the question ``Has data collection begun for this project?'', the answer to the question ``Have you looked at the data?'', and the text in the field ``Other comments''.
-Some users wrote in this field ``See the preregistration document specifying the logic, hypotheses, and analyses'' but that files is not made accessible.
+Some users wrote in this field ``See the preregistration document specifying the logic, hypotheses, and analyses'' but those files are not made accessible when the registration is made public after four years.
 If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the ``Other comments'' field.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bernal_social_1939}{}}%
-Bernal, J. D. (1939). \emph{The {Social Function Of Science}}. {London}: {Routledge}.
+Bernal, J. D. (1939). \emph{The social function of science}. {London}: {Routledge}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-chalmers_avoidable_2009}{}}%
-Chalmers, I., \& Glasziou, P. (2009). Avoidable waste in the production and reporting of research evidence. \emph{The Lancet}, \emph{374}(9683), 86--89.
+Chalmers, I., \& Glasziou, P.
+(2009).
+Avoidable waste in the production and reporting of research evidence.
+\emph{The Lancet}, \emph{374}(9683), 86--89.
+\url{https://doi.org/DOI:10.1016/S01406736(09)60329-9}
 
@@
 (1992).
-\href{https://www.ncbi.nlm.nih.gov/pubmed/1727960}{Factors influencing publication of research results.
-{Follow-up} of applications submitted to two institutional review boards}.
+Factors influencing publication of research results.
+{Follow-up} of applications submitted to two institutional review boards.
 \emph{JAMA}, \emph{267}(3), 374--378.
+\url{https://doi.org/10.1001/jama.1992.03480210049019}
 
@@
 (2012).
-The {Evolution} of {Trial Registries} and {Their Use} to {Assess} the {Clinical Trial Enterprise}.
+The evolution of trial registries and their use to assess the clinical trial enterprise.
 \emph{JAMA}, \emph{307}(17), 1861--1864.
@@
 (2010).
-Publication {Bias} in {Two Political Behavior Literatures}.
+Publication bias in two political behavior literatures.
 \emph{American Politics Research}, \emph{38}(4), 591--613.
@@
 (2021).
-Improving {Transparency}, {Falsifiability}, and {Rigor} by {Making Hypothesis Tests Machine-Readable}.
+Improving transparency, falsifiability, and rigor by making hypothesis tests machine-readable.
 \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(2), 2515245920970949.
@@
 (2021).
-Sorting the {File Drawer}: {A Typology} for {Describing Unpublished Studies}.
+Sorting the file drawer: {A} typology for describing unpublished studies.
 \emph{Perspectives on Psychological Science}, 1745691620979831.
@@
 (2017).
-Questionable, {Objectionable} or {Criminal}?
-{Public Opinion} on {Data Fraud} and {Selective Reporting} in {Science}.
+Questionable, objectionable or criminal?
+{Public} opinion on data fraud and selective reporting in science.
 \emph{Science and Engineering Ethics}, 1--21.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rosenthal_file_1979}{}}%
-Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638.
+Rosenthal, R.
+(1979).
+The file drawer problem and tolerance for null results.
+\emph{Psychological Bulletin}, \emph{86}(3), 638--641.
+https://doi.org/\href{https://\%20doi.org/10.1037/0033-2909.86.3.638}{https:// doi.org/10.1037/0033-2909.86.3.638}
 
@@
 (2021).
-An {Excess} of {Positive Results}: {Comparing} the {Standard Psychology Literature With Registered Reports}.
+An excess of positive results: {Comparing} the standard psychology literature with registered reports.
 \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(2), 25152459211007467.
@@
 (1959).
-Publication {Decisions} and {Their Possible Effects} on {Inferences Drawn} from {Tests} of {Significance--Or Vice Versa}.
+Publication decisions and their possible effects on inferences drawn from tests of significance--or vice versa.
 \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.

### 2023-06-18 supplement.Rmd
minor changes

@@
 abstract: |
-  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
+  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, the calculations to extrapolate from our sample to the population of registrations on the OSF before November 2017, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
 
@@
 As we did not email researchers when we felt confident the registration was not a research study, and as we did not receive replies from all researchers we emailed, the final classification has remaining uncertainty (see the discussion).
-
-We observed quite some variation in the amount of detail in the registrations that we examined.
-We therefore decided to code the ‘quality’ of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
-We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included).
-If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4.
-In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.
 
@@
 
-Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
-`r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration.
+We observed quite some variation in the amount of detail in the registrations that we examined.
+We therefore decided to code the extensiveness of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
+We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included).
+If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4.
+In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.
+`r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the goal or topic of the study was purely based on the registration.
 At least a minimal description was given for `r round(100*quality_reg[1,2]/sum(quality_reg[1,]),0)`% of the registrations in the manually opened registrations and `r round(100*quality_reg[2,2]/sum(quality_reg[2,]),0)`% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title).

### 2023-06-18 supplement.tex
minor changes

@@
 \abstract{%
-This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
+This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, the calculations to extrapolate from our sample to the population of registrations on the OSF before November 2017, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
 }
@@
 As we did not email researchers when we felt confident the registration was not a research study, and as we did not receive replies from all researchers we emailed, the final classification has remaining uncertainty (see the discussion).
-
-We observed quite some variation in the amount of detail in the registrations that we examined.
-We therefore decided to code the `quality' of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
-We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included).
-If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4.
-In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.
 
@@
 
-Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were.
-18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration.
+We observed quite some variation in the amount of detail in the registrations that we examined.
+We therefore decided to code the extensiveness of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents).
+We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included).
+If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4.
+In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.
+18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the goal or topic of the study was purely based on the registration.
 At least a minimal description was given for 36\% of the registrations in the manually opened registrations and 28\% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title).
